---
title: "MGT 6090 Assignment 6"
author: "Yuguang Shen"
date: "October 8, 2021"
output:
  pdf_document: default
  html_document: default
---

```{r, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidyquant)
library(lubridate)
library(janitor)
library(corrplot)
library(data.table)
library(gt)
library(knitr)
library(broom)
library(slider)
library(sandwich)
library(lmtest)

```

# 1. Useful functions 

## Beta calculation functions

```{r}

# Calculate beta, using cov and var

calc_beta <- function(my_df)
{
  result <- cov(my_df$ret_rf, my_df$mkt_rf) / var(my_df$mkt_rf)
  
  return (result)
}

# Winsorized version

calc_beta_w <- function(my_df)
{
  result <- cov(my_df$ret_rf_w, my_df$mkt_rf) / var(my_df$mkt_rf)
  
  return (result)
}

# Calculate beta for longer period

rolling_beta <- function(my_dt) 
{
  
result <-
  slide_period_vec(.x = my_dt, .i = my_dt$year, .period = "year", .f = function(my_dt){calc_beta(my_dt)}, .before = 1,   .complete = TRUE)

return (result)

}


rolling_beta_2 <- function(my_dt) 
{
  
result <-
  slide_period_vec(.x = my_dt, .i = my_dt$year, .period = "year", .f = function(my_dt){calc_beta(my_dt)}, .before = 2,   .complete = TRUE)

return (result)

}


rolling_beta_w <- function(my_dt) 
{
  
result <-
  slide_period_vec(.x = my_dt, .i = my_dt$year, .period = "year", .f = function(my_dt){calc_beta_w(my_dt)}, .before =    1, .complete = TRUE)

return (result)

}

```

## Usefule functions for statistics

```{r}

# Function to get n, mean, sd, ect

get_stats <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_n" = ~n(),
                        "_mean" = ~mean(., na.rm = TRUE), 
                        "_sd" = ~sd(., na.rm = TRUE),
                        "_skew" = ~skewness(., na.rm = TRUE),
                        "_kurt" = ~kurtosis(., na.rm = TRUE),
                        "_min" = ~min(., na.rm = TRUE),
                        "_max" = ~max(., na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "n, mean, sd, skewness, kurtosis, min, max") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = mean:max, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

# Function to get percentiles

get_percentiles <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_P1" = ~quantile(.,0.01, na.rm = TRUE),
                        "_P5" = ~quantile(.,0.05, na.rm = TRUE),
                        "_P25" = ~quantile(.,0.25, na.rm = TRUE),
                        "_P50" = ~quantile(.,0.5, na.rm = TRUE),
                        "_P75" = ~quantile(.,0.75, na.rm = TRUE),
                        "_P95" = ~quantile(.,0.95, na.rm = TRUE),
                        "_P99" = ~quantile(.,0.99, na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "percentiles") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = P1:P99, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

```

# 2. Load DSF and MSF data

```{r, message=FALSE, warning=FALSE}

dsf <- 
  fread("dsf_new.csv", select = c("PERMNO", "DATE", "RET", "VWRETD")) %>%
  filter(DATE >= 19940101) %>%
  clean_names() %>%
  mutate(date = ymd(date),
         ret = as.numeric(ret))

```

```{r, message=FALSE, warning=FALSE}

msf <-
  fread("msf_new2.csv", select = c("PERMNO", "DATE", "RET", "VWRETD", "PRC", "SHROUT")) %>%
  filter(DATE >= 19930101) %>%
  clean_names() %>%
  mutate(date = ymd(date),
         ret = as.numeric(ret),
         date = ceiling_date(date, "months") - 1,
         prc = abs(prc),
         mktcap = prc * shrout * 1000 / 1000000)

```

# 3. Calculate excess return for DSF and MSF dataset

## Load risk free rate data from Kenneth French data library

```{r, message=FALSE, warning=FALSE}

# Risk free rate in Kenneth French library is %. 
# Thus, it needs to be divided by 100 to match DSF and MSF

rf_monthly <-
  read_csv("F-F_Research_Data_Factors.csv", skip = 3) %>%
  rename("date" = "X1") %>%
  filter(date > 2020) %>%
  mutate(date = ymd(paste(date, "01"))) %>%
  mutate(date = ceiling_date(date, "months") - 1) %>%
  clean_names() %>%
  select(date, rf) %>%
  filter(date >= "1993-01-01") %>%
  mutate(rf = rf / 100)

```

```{r, message=FALSE, warning=FALSE}

rf_daily <-
  read_csv("F-F_Research_Data_Factors_daily.csv", skip = 4) %>%
  rename("date" = "X1") %>%
  clean_names() %>%
  select(date, rf) %>%
  mutate(date = ymd(date),
         rf = rf / 100) %>%
  filter(date >= "1994-01-01")

```

## Calculate excess return over risk free rate

```{r}

dsf <-
  left_join(dsf, rf_daily, by = c("date" = "date"))

```

```{r}

msf <-
  left_join(msf, rf_monthly, by = c("date" = "date"))

```

```{r}

dsf <-
  dsf %>%
  mutate(ret = ret - rf,
         vwretd = vwretd - rf) %>%
  rename("ret_rf" = "ret",
         "mkt_rf" = "vwretd") %>%
  select(-rf)

```

```{r}

msf <-
  msf %>%
  mutate(ret = ret - rf,
         vwretd = vwretd - rf) %>%
  rename("ret_rf" = "ret",
         "mkt_rf" = "vwretd") %>%
  select(-rf)
  
```

## Add column "year" to DSF and MSF

```{r}

dsf <-

  dsf %>%
  mutate(year = ceiling_date(date, "year") - 1) %>%
  relocate(year, .after = date) %>%
  na.omit()

```

```{r}

msf <-
 msf %>%
  mutate(year = ceiling_date(date, "year") - 1) %>%
  relocate(year, .after = date) %>%
  na.omit()

```

# 4. Estimate beta 

## 4.1 Beta using DSF

```{r}

# 1 month beta using DSF

dsf_betas <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(1), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_1m = calc_beta(cur_data())) %>%
  filter(year >= ymd("1995-12-31")) %>%
  select(permno, year, beta_1m) %>%
  distinct()

```

```{r}

# 3 month beta using DSF

dsf_betas <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(3), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_3m = calc_beta(cur_data())) %>%
  select(permno, year, beta_3m) %>%
  distinct() %>%
  left_join(dsf_betas, ., by = c("permno" = "permno", "year" = "year"))

```

```{r}

# 6 month beta using DSF

dsf_betas <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(6), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_6m = calc_beta(cur_data())) %>%
  select(permno, year, beta_6m) %>%
  distinct() %>%
  left_join(dsf_betas, ., by = c("permno" = "permno", "year" = "year"))

```

```{r}

# 12 month beta using DSF

dsf_betas <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(12), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_12m = calc_beta(cur_data())) %>%
  select(permno, year, beta_12m) %>%
  distinct() %>%
  left_join(dsf_betas, ., by = c("permno" = "permno", "year" = "year"))

```

```{r, message=FALSE, warning=FALSE}

# 24 month beta using DSF

dsf_beta_24m <- 
  dsf %>%
  group_by(permno) %>%
  summarise(beta_24m = rolling_beta(cur_data()%>%group_by(year)),
            my_year = unique(year)) %>%
  na.omit()

```

### Combine dsf betas

```{r}

dsf_betas <-

left_join(dsf_betas, dsf_beta_24m, by = c("permno" = "permno", "year" = "my_year"))

```

## 4.2 Beta using MSF dataset

```{r}

# 12 month beta using MSF

msf_betas <-

msf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(12), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_1y = calc_beta(cur_data())) %>%
  filter(year >= ymd("1995-12-31")) %>%
  select(permno, year, beta_1y) %>%
  distinct()

```

```{r, message=FALSE, warning=FALSE}

# 24 month beta using MSF

msf_beta_2y <-

msf %>%
  group_by(permno) %>%
  summarise(beta_2y = rolling_beta(cur_data()%>%group_by(year)),
            my_year = unique(year)) %>%
  na.omit()

```

```{r, message=FALSE, warning=FALSE}

# 36 month beta using MSF

msf_beta_3y <-

msf %>%
  group_by(permno) %>%
  summarise(beta_3y = rolling_beta_2(cur_data()%>%group_by(year)),
            my_year = unique(year)) %>%
  na.omit()

```

### Combine msf betas

```{r}
msf_betas <-
  
left_join(msf_betas, msf_beta_2y, by = c("permno" = "permno", "year" = "my_year") ) %>%
  left_join(., msf_beta_3y, by = c("permno" = "permno", "year" = "my_year")) 

```

## 4.3 Beta using winsorized DSF dataset

### Winsorize DSF dataset

```{r}

dsf <-
  
dsf %>%
  mutate(ret_rf_w = case_when(mkt_rf>0 & ret_rf>4*mkt_rf ~ 4*mkt_rf,
                              mkt_rf>0 & ret_rf<(-2)*mkt_rf ~ (-2)*mkt_rf,
                              mkt_rf<0 & ret_rf>(-2)*mkt_rf ~ (-2)*mkt_rf,
                              mkt_rf<0 & ret_rf<4*mkt_rf ~ 4*mkt_rf,
                              TRUE ~ ret_rf))

```

### Winsorize betas

```{r}

# 1 month beta using winsorized DSF

dsf_betas_w <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(1), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_1m = calc_beta_w(cur_data())) %>%
  filter(year >= ymd("1995-12-31")) %>%
  select(permno, year, beta_1m) %>%
  distinct()

dsf_betas_w <-
  dsf_betas_w %>%
  rename("beta_1m_w" = "beta_1m")

```

```{r}

# 3 month beta using winsorized DSF

dsf_betas_w <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(3), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_3m_w = calc_beta_w(cur_data())) %>%
  select(permno, year, beta_3m_w) %>%
  distinct() %>%
  left_join(dsf_betas_w, ., by = c("permno" = "permno", "year" = "year"))

```

```{r}

# 6 month beta using winsorized DSF

dsf_betas_w <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(6), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_6m_w = calc_beta_w(cur_data())) %>%
  select(permno, year, beta_6m_w) %>%
  distinct() %>%
  left_join(dsf_betas_w, ., by = c("permno" = "permno", "year" = "year"))

```

```{r}

# 12 month beta using winsorized DSF

dsf_betas_w <-

dsf %>%
  group_by(permno) %>%
  filter(date %within% interval(year %m-% months(12), year)) %>%
  group_by(permno, year) %>%
  mutate(beta_12m_w = calc_beta_w(cur_data())) %>%
  select(permno, year, beta_12m_w) %>%
  distinct() %>%
  left_join(dsf_betas_w, ., by = c("permno" = "permno", "year" = "year"))

```

```{r, message=FALSE, warning=FALSE}

# 24 month beta using winsorized DSF

dsf_beta_24m_w <-
  dsf %>%
  group_by(permno) %>%
  summarise(beta_24m_w = rolling_beta_w(cur_data()%>%group_by(year)),
            my_year = unique(year)) %>%
  na.omit()
  
```

### Combine winsorized beta files

```{r}

dsf_betas_w <-

left_join(dsf_betas_w, dsf_beta_24m_w, by = c("permno" = "permno", "year" = "my_year"))

```

## 4.4 Combine dsf, msf, and winsorized dsf betas

```{r}

betas <-
  left_join(dsf_betas, dsf_betas_w, by = c("permno" = "permno", "year" = "year")) %>%
  left_join(., msf_betas, by = c("permno" = "permno", "year" = "year"))
  
```

# 5. Descriptive statistics for betas

```{r}

columns_of_interest <-
  betas %>%
  ungroup() %>%
  select(-c(permno, year)) %>%
  colnames()
 
get_stats(betas, NULL, columns_of_interest)
 
get_percentiles(betas, NULL, columns_of_interest)
 
```

# 6. Correlation of betas

```{r}

betas %>%
  ungroup() %>%
  select(beta_1m:beta_3y) %>%
  cor(use="complete.obs") %>%
  corrplot(method = "pie",
           order = "AOE",
           tl.cex = 0.6,
           title = "Correlation of Betas",
           number.cex = 0.6,
           addCoef.col = 'black',
           mar=c(0,0,1,0))

```

# 7. CAPM, beta and stock return

## Deciles of beta (choose beta_24m_w)

```{r}

beta_deciles <-
  
  betas %>%
  select(permno, year, beta_24m_w) %>%
  ungroup() %>%
  mutate(beta_rank = ntile(beta_24m_w, 10))

```


```{r}

# Avg beta, avg return

yearly_return_data <-
  
msf %>%
  group_by(permno, year) %>%
  summarise(avg_ret = mean(ret_rf),
            avg_cap = mean(mktcap),
            avg_mkt_ret = mean(mkt_rf)) %>%
  left_join(., beta_deciles, by = c("permno" = "permno", "year" = "year")) %>%
  na.omit()

```
## Equal weighted

```{r, message=FALSE, warning=FALSE}

equal_weighted <-
  
yearly_return_data %>%
  group_by(beta_rank, year) %>%
  summarise(portfolio_return = mean(avg_ret),
            mkt_return = mean(avg_mkt_ret),
            portfolio_beta = mean(beta_24m_w))

```


```{r}

equal_weighted_summary <-
  equal_weighted %>%
  group_by(beta_rank) %>%
  summarise(return_summary = mean(portfolio_return),
            beta_summary = mean(portfolio_beta))

gt(equal_weighted_summary) %>%
   tab_header(title = "Summary for Equal Weighted Portfolios")

```

## Value weighted

```{r, message=FALSE, warning=FALSE}

value_weighted <-
  
yearly_return_data %>%
  group_by(beta_rank, year) %>%
  summarise(portfolio_return = sum(avg_ret*avg_cap/sum(avg_cap)),
            mkt_return = mean(avg_mkt_ret),
            portfolio_beta = sum(beta_24m_w*avg_cap/sum(avg_cap))) 


```

```{r}

value_weighted_summary <-
  value_weighted %>%
  group_by(beta_rank) %>%
  summarise(return_summary = mean(portfolio_return),
            beta_summary = mean(portfolio_beta))

gt(value_weighted_summary) %>%
   tab_header(title = "Summary for Value Weighted Portfolios")

```


# 8. Hypothesis test

## Equal weighted portfolio hypothesis test

```{r}

print("Hypothesis test for Equal Weighted portfolio:")

for (i in 1:10)
{
  temp_portfolio <-
    equal_weighted %>%
    filter(beta_rank == i)
  
  
  nw_vcov <-
    NeweyWest(lm(temp_portfolio$portfolio_return ~ temp_portfolio$mkt_return),
              lag = 5, prewhite = FALSE,
              adjust = TRUE)
  
  temp_model <-
    lm(temp_portfolio$portfolio_return ~ temp_portfolio$mkt_return)
  
  model_adjusted <-
    coeftest(temp_model, vcov = nw_vcov)
  
  print("For beta_rank = ")
  print(i)
  print(model_adjusted)
  
}



```

## Value weighted portfolio hypothesis test

```{r}

print("Hypothesis test for Value Weighted Portfolio: ")

for (i in 1:10)
{
  temp_portfolio <-
    value_weighted %>%
    filter(beta_rank == i)
  
  
  nw_vcov <-
    NeweyWest(lm(temp_portfolio$portfolio_return ~ temp_portfolio$mkt_return),
              lag = 5, prewhite = FALSE,
              adjust = TRUE)
  
  temp_model <-
    lm(temp_portfolio$portfolio_return ~ temp_portfolio$mkt_return)
  
  model_adjusted <-
    coeftest(temp_model, vcov = nw_vcov)
  
  print("For beta_rank = ")
  print(i)
  print(model_adjusted)
  
}



```


