---
title: "MGT 6090 Assignment 5 Part 2: Agrregate monthly return from DSF daily return"
author: "Yuguang Shen"
date: "September 30, 2021"
output:
  pdf_document: default
  html_document: default
---

```{r, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidyquant)
library(lubridate)
library(janitor)
library(corrplot)
library(data.table)
library(patchwork)
library(gt)
library(knitr)
library(RColorBrewer)
library(data.table)

```

# Load DSF dataset

```{r}

# data.table package is good for large dataset

dsf_ret <- 
  fread("dsf_new.csv", select = c("PERMNO", "DATE", "SHRCD", "RET", "VWRETD")) %>%
  filter(SHRCD %in% c(10, 11)) %>%
  select(-SHRCD) %>% 
  clean_names()

```

# Add features, such as Month, Excess Return over Mkt, and Excess Log Return over Mkt

```{r, message=FALSE, warning=FALSE}

dsf_ret <-
  
dsf_ret %>%
  mutate(ret = as.numeric(ret),
         ret_mkt = ret - vwretd,
         date_month = ceiling_date(ymd(date), "months") - 1,
         ret_mkt_log = log(1 + ret_mkt))

dsf_ret <-
  
  dsf_ret %>%
  mutate(date = ymd(date))

```

# Compute monthly Compounded Excess Return and Cumulative Log Excess Return 

```{r, message=FALSE, warning=FALSE}

# Save it as a new dataset for monthly aggregate return data only
# Monthly compounded return is the product of (1 + daily return) in that month, then minus 1
# Monthly cumulative log return is sum of daily log return in that month

monthly_aggregate_ret <-

dsf_ret %>%
  group_by(permno, date_month) %>%
  summarise(trading_days = n(),
            cmpd_ret_mkt = prod(1 + ret_mkt, na.rm = TRUE) - 1,
            cumu_ret_mkt_log = sum(ret_mkt_log, na.rm = TRUE))

```

# Useful Functions for Statistics

```{r}

# Calculate n, mean, sd, ect

get_stats <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_n" = ~n(),
                        "_mean" = ~mean(., na.rm = TRUE), 
                        "_sd" = ~sd(., na.rm = TRUE),
                        "_skew" = ~skewness(., na.rm = TRUE),
                        "_kurt" = ~kurtosis(., na.rm = TRUE),
                        "_min" = ~min(., na.rm = TRUE),
                        "_max" = ~max(., na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "n, mean, sd, skewness, kurtosis, min, max") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = mean:max, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

# Calculate percentile

get_percentiles <- function(my_df, col_0 = NULL, col_1) {
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_P1" = ~quantile(.,0.01, na.rm = TRUE),
                        "_P5" = ~quantile(.,0.05, na.rm = TRUE),
                        "_P25" = ~quantile(.,0.25, na.rm = TRUE),
                        "_P50" = ~quantile(.,0.5, na.rm = TRUE),
                        "_P75" = ~quantile(.,0.75, na.rm = TRUE),
                        "_P95" = ~quantile(.,0.95, na.rm = TRUE),
                        "_P99" = ~quantile(.,0.99, na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "percentiles") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = P1:P99, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

```


# Descriptive stats of monthly aggregate Returns, 1925-2020

```{r}

monthly_aggregate_ret %>%
  filter(date_month > "1925-01-01") %>%
  get_stats(NULL, c("cmpd_ret_mkt", "cumu_ret_mkt_log"))

monthly_aggregate_ret %>%
  filter(date_month > "1925-01-01") %>%
  get_percentiles(NULL, c("cmpd_ret_mkt", "cumu_ret_mkt_log"))

```

# Descriptive stats of monthly aggregate Returns, 1963-2020

```{r}

monthly_aggregate_ret %>%
  filter(date_month > "1963-01-01") %>%
  get_stats(NULL, c("cmpd_ret_mkt", "cumu_ret_mkt_log"))

monthly_aggregate_ret %>%
  filter(date_month > "1963-01-01") %>%
  get_percentiles(NULL, c("cmpd_ret_mkt", "cumu_ret_mkt_log"))


```

# Plot monthly mean and sd for Compounded Excess Return over Market

```{r}

cmpd_ret_stats_table <-
  monthly_aggregate_ret %>%
  get_stats("date_month", "cmpd_ret_mkt") 

cmpd_ret_stats_table$`_data` %>%
  select(date_month, mean, sd) %>%
  pivot_longer(-date_month, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date_month, value, colour = variable)) +
  geom_line() +
  labs(title = "Monthly Mean and Sd of Compounded Excess Return over Market")

```

# Plot monthly mean and sd for Cumulative Excess Log Return over Market

```{r}

cumu_ret_log_stats_table <-
  monthly_aggregate_ret %>%
  get_stats("date_month", "cumu_ret_mkt_log") 

cumu_ret_log_stats_table$`_data` %>%
  select(date_month, mean, sd) %>%
  pivot_longer(-date_month, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date_month, value, colour = variable)) +
  geom_line() +
  labs(title = "Monthly Mean and Sd of Cumulative Excess Log Return over Market")

```