---
title: "MGT 6090 Assignment 8"
author: "Yuguang Shen"
date: "October 25, 2021"
output:
  pdf_document: default
  html_document: default
---

```{r, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidyquant)
library(lubridate)
library(janitor)
library(data.table)
library(gt)
library(slider)
library(zoo)
library(broom)
library(corrplot)
library(scales)

```

# Random 10 years and 250 firms

## Random year

seed = 903679462
random_year = 2010

The time period of this project will be 2010-2019

```{r}

set.seed(903679462)

random_year <- 
  sample(1980:2010, size = 1)

```

## 250 firms

The first trading day of 2010 is 20100104

```{r}

# Create a pool of firms as of 2010-01-04

firm_pool <-
  
fread("dsf_new.csv", select = c("DATE", "PERMNO")) %>%
  clean_names() %>%
  filter(date == 20100104) %>%
  select(permno)
  
```

```{r}

# Choose 250 firms from the pool

set.seed(903679462)

chosen_firms <-
  
firm_pool[sample(nrow(firm_pool), 250), ]

```

## Import data from DSF dataset

```{r, message=FALSE, warning=FALSE}

# Import DSF data

dsf_hw8 <-

fread("dsf_new.csv", select = c("DATE", "PERMNO", "RET", "VWRETD")) %>%
  clean_names() %>%
  filter((date >= 20100101 & date <= 20191231) & permno %in% chosen_firms$permno) %>%
  mutate(ret = as.numeric(ret)) %>%
  na.omit()


```

```{r, message=FALSE, warning=FALSE}

# Import F-F daily risk-free rate

my_url <- "https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/F-F_Research_Data_Factors_daily_CSV.zip"

my_file <- tempfile()

download.file(my_url, my_file)

ff_daliy_rf <- 
  read_csv(unzip(my_file), skip = 4) %>%
  clean_names() %>%
  rename("date" = "x1") %>%
  mutate(rf = rf / 100) %>% 
  select(date, rf) %>%
  filter(date >= 20100101 & date <= 20191231)

```

```{r}

# Combine DSF data with daily risk-free rate

dsf_hw8 <-
  
left_join(dsf_hw8, ff_daliy_rf, by = c("date" = "date"))

```

# Semi beta, downside beta, co-skewness and tail risk

## Add features: year_month, ret_rf, mkt_rf, r_tki, f_tk, r_tki_plus, r_tki_minus, f_tk_plus, f_tk_minus

```{r}

# Add more features: year_month, ret_rf, mkt_rf

dsf_hw8 <-
  
dsf_hw8 %>%
  mutate(date = ymd(date),
         year_month = ceiling_date(date, "months") - 1,
         ret_rf = ret - rf,
         mkt_rf = vwretd - rf) %>%
  relocate(date, .after = permno) %>%
  relocate(year_month, .after = date)

```


```{r}

# Add more features: r_tki, f_tk

dsf_hw8 <-

dsf_hw8 %>%
  group_by(permno, year_month) %>%
  mutate( r_tki = ret_rf - mean(ret_rf),
          f_tk = mkt_rf - mean(mkt_rf))

```


```{r}

# Add more features: r_tki_plus, r_tki_minus, f_tk_plus, f_tk_minus

dsf_hw8 <-

dsf_hw8 %>%
  mutate(r_tki_plus = case_when(r_tki > 0 ~ r_tki,
                                TRUE ~ 0),
         r_tki_minus = case_when(r_tki < 0 ~ r_tki,
                                 TRUE ~ 0),
         f_tk_plus = case_when(f_tk > 0 ~ f_tk,
                               TRUE ~ 0),
         f_tk_minus = case_when(f_tk < 0 ~ f_tk,
                                TRUE ~ 0))
  
```


## Calculate beta, co_skewness and co_kurtosis

```{r, message=FALSE, warning=FALSE}

betas_skew_kurt <-

dsf_hw8 %>%
  group_by(permno, year_month) %>%
  summarise(beta_N = sum(r_tki_minus * f_tk_minus) / sum(f_tk * f_tk),
            beta_P = sum(r_tki_plus * f_tk_plus) / sum(f_tk * f_tk),
            beta_M_minus = - sum(r_tki_plus * f_tk_minus) / sum(f_tk * f_tk),
            beta_M_plus = - sum(r_tki_minus * f_tk_plus) / sum(f_tk * f_tk),
            beta = sum(r_tki * f_tk) / sum(f_tk * f_tk),
            beta_sum = beta_N + beta_P - beta_M_plus - beta_M_minus,
            beta_down = sum(r_tki * f_tk_minus) / sum(f_tk_minus * f_tk_minus),
            beta_up = sum(r_tki * f_tk_plus) / sum(f_tk_plus * f_tk_plus),
            m = n(),
            co_skew = (sum(r_tki * f_tk * f_tk) / m) / (sqrt(sum(r_tki*r_tki) / m) * (sum(f_tk*f_tk) / m)),
            co_kurt = (sum(r_tki * (f_tk^3)) / m) / sqrt(sum(r_tki^2) / m * (sum(f_tk^2) / m)^3)) %>%
  na.omit()

```

## Analyze returns based on downside beta, upside beta, coskewness, and cokurtosis

Every time tocks are divided into four portfolios, each of which is equaly weighted, according to 25th, 50th, and 75th percentile rankings of various risk measures. The monthly portfolio returns are ploted. The mean monthly return for each portfolio is calculated and then annulized. 

```{r}

# Rank the stocks based on downside beta, upside beta, coskewness, and cokurtosis

ranks <-
betas_skew_kurt %>%
  ungroup() %>%
  select(permno, year_month, beta_down, beta_up, co_skew, co_kurt) %>%
  group_by(year_month) %>%
  mutate(beta_down_rank = case_when(beta_down <= quantile(cur_data()$beta_down, 0.25) ~ 1,
                                    beta_down <= quantile(cur_data()$beta_down, 0.5) & 
                                    beta_down > quantile(cur_data()$beta_down, 0.25) ~ 2,
                                    beta_down <= quantile(cur_data()$beta_down, 0.75) & 
                                      beta_down > quantile(cur_data()$beta_down, 0.5) ~ 3,
                                    TRUE ~ 4),
         beta_up_rank = case_when(beta_up <= quantile(cur_data()$beta_up, 0.25) ~ 1,
                                    beta_up <= quantile(cur_data()$beta_up, 0.5) & 
                                    beta_up > quantile(cur_data()$beta_up, 0.25) ~ 2,
                                    beta_up <= quantile(cur_data()$beta_up, 0.75) & 
                                      beta_up > quantile(cur_data()$beta_up, 0.5) ~ 3,
                                    TRUE ~ 4),
         co_skew_rank = case_when(co_skew <= quantile(cur_data()$co_skew, 0.25) ~ 1,
                                    co_skew <= quantile(cur_data()$co_skew, 0.5) & 
                                    co_skew > quantile(cur_data()$co_skew, 0.25) ~ 2,
                                    co_skew <= quantile(cur_data()$co_skew, 0.75) & 
                                      co_skew > quantile(cur_data()$co_skew, 0.5) ~ 3,
                                    TRUE ~ 4),
         co_kurt_rank = case_when(co_kurt <= quantile(cur_data()$co_kurt, 0.25) ~ 1,
                                    co_kurt <= quantile(cur_data()$co_kurt, 0.5) & 
                                    co_kurt > quantile(cur_data()$co_kurt, 0.25) ~ 2,
                                    co_kurt <= quantile(cur_data()$co_kurt, 0.75) & 
                                      co_kurt > quantile(cur_data()$co_kurt, 0.5) ~ 3,
                                    TRUE ~ 4))


```

```{r}

# Combine ranking data with return data

ret_w_rank <-
dsf_hw8 %>%
  select(permno : ret) %>%
  left_join(., ranks %>% select(permno, year_month, beta_down_rank : co_kurt_rank), by = c("permno" = "permno", "year_month" = "year_month")) %>%
  na.omit()

```

### Based on Downside Beta

```{r, message=FALSE, warning=FALSE}

# Monthly portfolio returns based on downside beta rank

rank_by_down_beta <-
ret_w_rank %>%
  select(date, year_month, ret, beta_down_rank) %>%
  group_by(beta_down_rank, date) %>% 
  summarise(ret_daily = mean(ret),
            year_month = year_month) %>%
  distinct() %>%
  ungroup() %>%
  group_by(beta_down_rank, year_month) %>%
  summarise(ret_monthly_pct = (prod(cur_data()$ret_daily+1) - 1) * 100)

```

```{r}

# Plot monthly return of portfolios based on downside beta rank

rank_by_down_beta %>%
  ggplot(aes(x = year_month, y = ret_monthly_pct, color = as.character(beta_down_rank))) +
  geom_line() +
  labs(title = "Monthly Portfolio Return",
       subtitle = "Based on Downside Beta Rank", 
       color = "downside beta rank (1:4 low:high)", 
       y = "Monthly Returns (%)",
       x = "") +
  scale_y_continuous(breaks = breaks_pretty(n = 10)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))

```

```{r}

# Calculate annualized return of portfolio based on downside beta ranking and make a table

rank_by_down_beta %>%
  ungroup() %>%
  group_by(beta_down_rank) %>%
  summarise(annual_ret_pct = mean(ret_monthly_pct) * 12,
            annual_ret_sd = sd(ret_monthly_pct) * sqrt(12)) %>%
  gt() %>%
  tab_header(title = "Annualized Portforlio Return",
             subtitle = "Based on Downside Beta Ranking") %>%
  cols_align(align = "center", columns = everything()) %>%
  fmt_number(columns = c(annual_ret_pct, annual_ret_sd), decimals = 2)

```

### Based on Upside Beta

```{r, message=FALSE, warning=FALSE}

# Monthly portfolio returns based on upside beta rank

rank_by_up_beta <-
ret_w_rank %>%
  select(date, year_month, ret, beta_up_rank) %>%
  group_by(beta_up_rank, date) %>% 
  summarise(ret_daily = mean(ret),
            year_month = year_month) %>%
  distinct() %>%
  ungroup() %>%
  group_by(beta_up_rank, year_month) %>%
  summarise(ret_monthly_pct = (prod(cur_data()$ret_daily+1) - 1) * 100)

```

```{r}

# Plot monthly return of portfolios based on upside beta rank

rank_by_up_beta %>%
  ggplot(aes(x = year_month, y = ret_monthly_pct, color = as.character(beta_up_rank))) +
  geom_line() +
  labs(title = "Monthly Portfolio Return",
       subtitle = "Based on Upside Beta Rank", 
       color = "upside beta rank (1:4 low:high)", 
       y = "Monthly Returns (%)",
       x = "") +
  scale_y_continuous(breaks = breaks_pretty(n = 10)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))

```

```{r}

# Calculate annualized return of portfolio based on upside beta ranking and make a table

rank_by_up_beta %>%
  ungroup() %>%
  group_by(beta_up_rank) %>%
  summarise(annual_ret_pct = mean(ret_monthly_pct) * 12,
            annual_ret_sd = sd(ret_monthly_pct) * sqrt(12)) %>%
  gt() %>%
  tab_header(title = "Annualized Portforlio Return",
             subtitle = "Based on Upside Beta Ranking") %>%
  cols_align(align = "center", columns = everything()) %>%
  fmt_number(columns = c(annual_ret_pct, annual_ret_sd), decimals = 2)

```

### Based on Coskewness

```{r, message=FALSE, warning=FALSE}

# Monthly portfolio returns based on coskewness rank

rank_by_co_skew <-
ret_w_rank %>%
  select(date, year_month, ret, co_skew_rank) %>%
  group_by(co_skew_rank, date) %>% 
  summarise(ret_daily = mean(ret),
            year_month = year_month) %>%
  distinct() %>%
  ungroup() %>%
  group_by(co_skew_rank, year_month) %>%
  summarise(ret_monthly_pct = (prod(cur_data()$ret_daily+1) - 1) * 100)

```

```{r}

# Plot monthly return of portfolios based on coskewness rank

rank_by_co_skew %>%
  ggplot(aes(x = year_month, y = ret_monthly_pct, color = as.character(co_skew_rank))) +
  geom_line() +
  labs(title = "Monthly Portfolio Return",
       subtitle = "Based on Coskewness Rank", 
       color = "coskewness rank (1:4 low:high)", 
       y = "Monthly Returns (%)",
       x = "") +
  scale_y_continuous(breaks = breaks_pretty(n = 10)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))

```

```{r}

# Calculate annualized return of portfolio based on coskewness ranking and make a table

rank_by_co_skew %>%
  ungroup() %>%
  group_by(co_skew_rank) %>%
  summarise(annual_ret_pct = mean(ret_monthly_pct) * 12,
            annual_ret_sd = sd(ret_monthly_pct) * sqrt(12)) %>%
  gt() %>%
  tab_header(title = "Annualized Portforlio Return",
             subtitle = "Based on Coskewness Ranking") %>%
  cols_align(align = "center", columns = everything()) %>%
  fmt_number(columns = c(annual_ret_pct, annual_ret_sd), decimals = 2)

```

### Based on Cokurtosis 

```{r, message=FALSE, warning=FALSE}

# Monthly portfolio returns based on cokurtosis rank

rank_by_co_kurt <-
ret_w_rank %>%
  select(date, year_month, ret, co_kurt_rank) %>%
  group_by(co_kurt_rank, date) %>% 
  summarise(ret_daily = mean(ret),
            year_month = year_month) %>%
  distinct() %>%
  ungroup() %>%
  group_by(co_kurt_rank, year_month) %>%
  summarise(ret_monthly_pct = (prod(cur_data()$ret_daily+1) - 1) * 100)

```

```{r}

# Plot monthly return of portfolios based on cokurtosis rank

rank_by_co_kurt %>%
  ggplot(aes(x = year_month, y = ret_monthly_pct, color = as.character(co_kurt_rank))) +
  geom_line() +
  labs(title = "Monthly Portfolio Return",
       subtitle = "Based on Cokurtosis Rank", 
       color = "cokurtosis rank (1:4 low:high)", 
       y = "Monthly Returns (%)",
       x = "") +
  scale_y_continuous(breaks = breaks_pretty(n = 10)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5))

```

```{r}

# Calculate annualized return of portfolio based on cokurtosis ranking and make a table

rank_by_co_kurt %>%
  ungroup() %>%
  group_by(co_kurt_rank) %>%
  summarise(annual_ret_pct = mean(ret_monthly_pct) * 12,
            annual_ret_sd = sd(ret_monthly_pct) * sqrt(12)) %>%
  gt() %>%
  tab_header(title = "Annualized Portforlio Return",
             subtitle = "Based on Cokurtosis Ranking") %>%
  cols_align(align = "center", columns = everything()) %>%
  fmt_number(columns = c(annual_ret_pct, annual_ret_sd), decimals = 2)

```


## Correlation of Beta Measures

```{r}

betas_skew_kurt %>%
  ungroup() %>%
  select(-c(permno, year_month, m)) %>%
  cor() %>%
  corrplot(method = "pie",
           title = "Correlation of Beta Measures", 
           number.cex = 0.6,
           addCoef.col = 'black', 
           mar=c(0,0,1,0))

```

# VaR and ES

## From 2010-01-01 to 2019-12-31

```{r}

# Calculate the daily return of this equal-weighted portfolio through this period
# Some stocks may cease to exist in this period. Check the number of stocks daily and adjust the weight accordingly.

portfolio_return_1 <-

dsf_hw8 %>%
  ungroup() %>%
  select(date, permno, ret) %>%
  group_by(date) %>%
  summarise(n_stocks = n(),
            port_ret = sum(ret) / n_stocks)

```

```{r}

# Visualize the daily return of this portfolio

portfolio_return_1 %>%
  ggplot(aes(port_ret)) +
  geom_density(color = "steelblue") + 
  geom_vline(xintercept = quantile(portfolio_return_1$port_ret, probs = 0.05)) +
  labs(title = "Portfolio one-day 5% VaR from 2010-01-01 to 2019-12-31",
       x = "portforlio return") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = .5))
  

```


```{r}

# Find the 5% quantile

var_1 <-
  quantile(portfolio_return_1$port_ret, probs = 0.05)

dollar_var_1 <- 
  var_1 * 250

es_1 <- 
  mean(portfolio_return_1$port_ret[portfolio_return_1$port_ret < var_1])

dollar_es_1 <-
  es_1 * 250

```

```{r}

# Make a table for VaR and ES result

data.frame(var_1, dollar_var_1, es_1, dollar_es_1) %>%
  rename("VaR" = "var_1", "Dollar_VaR_mil" = "dollar_var_1", "ES" = "es_1", "Dollar_ES_mil" = "dollar_es_1") %>%
  gt() %>%
  tab_header(title = "Portfolio one-day 5% VaR and ES from 2010-01-01 to 2019-12-31 ") %>% 
  cols_align(align = "center", columns = everything()) %>%
  fmt_number(columns = everything(), decimals = 4)

```

## From 2000-01-01 to 2010-12-31

```{r, message=FALSE, warning=FALSE}

# Calculate the daily return of this equal weight portfolio.
# The number of stocks availabe on each day varies.

portfolio_return_2 <-

fread("dsf_new.csv", select = c("DATE", "PERMNO", "RET")) %>%
  clean_names() %>%
  filter((date >= 20000101 & date <= 20101231) & permno %in% chosen_firms$permno) %>%
  mutate(date = ymd(date),
         ret = as.numeric(ret)) %>%
  na.omit() %>%
  group_by(date) %>%
  summarise(n_stocks = n(),
            port_ret = sum(ret) / n_stocks)

```

```{r}

# Visualize the daily return of this portfolio

portfolio_return_2 %>%
  ggplot(aes(port_ret)) +
  geom_density(color = "steelblue") + 
  geom_vline(xintercept = quantile(portfolio_return_2$port_ret, probs = 0.05)) +
  labs(title = "Portfolio one-day 5% VaR from 2000-01-01 to 2010-12-31",
       x = "portforlio return") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = .5))


```

```{r}

# Calculate VaR and ES

var_2 <-
  quantile(portfolio_return_2$port_ret, probs = 0.05)

dollar_var_2 <- 
  var_2 * 250

es_2 <- 
  mean(portfolio_return_2$port_ret[portfolio_return_2$port_ret < var_2])

dollar_es_2 <-
  es_2 * 250

```

```{r}

# Make a table for VaR and ES result

data.frame(var_2, dollar_var_2, es_2, dollar_es_2) %>%
  rename("VaR" = "var_2", "Dollar_VaR_mil" = "dollar_var_2", "ES" = "es_2", "Dollar_ES_mil" = "dollar_es_2") %>%
  gt() %>%
  tab_header(title = "Portfolio one-day 5% VaR and ES from 2000-01-01 to 2010-12-31 ") %>% 
  cols_align(align = "center", columns = everything()) %>%
  fmt_number(columns = everything(), decimals = 4)

```


# Volatility modeling

## Simple Risk Metrics Model

```{r}

# Calculate annualized variance of 250 chosen stocks
# Do not annualize

initial_variance <-

dsf_hw8 %>%
  ungroup() %>%
  select(permno, ret) %>%
  group_by(permno) %>%
  summarise(variance = var(ret))

initial_variance %>%
  ungroup() %>%
  gt() %>%
  tab_header(title = "Initial Variance for Each Firm") %>%
  cols_align(align = "center", columns = everything()) 

```

```{r}

# Randomly choose 5 stocks from 250 chosen stocks

set.seed(903679462)

five_firms <-
  
chosen_firms[sample(nrow(chosen_firms), 5), ]

```

```{r, message=FALSE, warning=FALSE}

# Import return data for these 5 firms from 2000-01-01 to 2010-12-31

return_five_firms <-

fread("dsf_new.csv", select = c("DATE", "PERMNO", "RET")) %>%
  clean_names() %>%
  filter((date >= 20000101 & date <= 20101231) & permno %in% five_firms$permno) %>%
  mutate(ret = as.numeric(ret)) %>%
  na.omit()

```


```{r}

# Add initial variance to each of the 5 firms

return_five_firms <-

left_join(return_five_firms[, .SD[1], by = permno], initial_variance[initial_variance$permno %in% five_firms$permno, ], by = c("permno" = "permno")) %>%
  left_join(return_five_firms, ., by = c("permno" = "permno", "date" = "date", "ret" = "ret"))

```

```{r}

# Apply the recursive formula to calculate variance according to the variance of previous day

for (i in 2:nrow(return_five_firms))
{
   return_five_firms$variance[i] = if_else (is.na(return_five_firms$variance[i]), 0.94 * return_five_firms$variance[i-1] + 0.06 * (return_five_firms$ret[i-1])^2,
                                 return_five_firms$variance[i])
}

```

```{r}

# Plot the time series of variance by JP Morgan's Risk Metrics for each of the 5 firms

return_five_firms %>%
  mutate(date = ymd(date)) %>%
  group_by(date, permno) %>%
  ggplot(aes(x = date, y = variance)) +
  geom_line() +
  facet_wrap(~ permno, scales = "free", nrow = 3, ncol = 3) +
  labs(title = "Variance by JP Morgan's Risk Metrics") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = .5))

```

## GARCH

```{r}

# Calculate historical variance of rolling 25-day window for all 250 firms

initial_variance_garch <-
  
  dsf_hw8 %>%
  ungroup() %>%
  select(permno, ret) %>%
  group_by(permno) %>%
  mutate(variance_25 = rollapply(cur_data(), 25, FUN = var, align = "right", partial = FALSE, fill = NA),
         variance_25_lag = lag(variance_25, 1))

```

```{r}

# Use linear regression to get omega, beta, and alpha for each firm

garch_coef <-

initial_variance_garch %>%
  group_by(permno) %>%
  na.omit() %>%
  nest() %>%
  mutate(models = map(data, ~ lm(variance_25 ~ variance_25_lag + ret, data = .x)),
         tidied = map(models, tidy)
         ) %>%
  unnest(tidied) %>%
  select(permno, term, estimate) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>%
  rename("omega" = "(Intercept)", "beta" = "variance_25_lag", "alpha" = "ret")

garch_coef %>%
  ungroup() %>%
  gt() %>%
  tab_header(title = "GARCH (1,1) Model Parameters for Each Firm") %>%
  cols_align(align = "center", columns = everything()) 
  
```

```{r}

# Get GARCH model coefficients for the five firms

garch_coef_five_firms <-
  garch_coef %>%
  filter(permno %in% five_firms$permno)

```

```{r, message=FALSE, warning=FALSE}

# Import return data for these 5 firms from 2000-01-01 to 2010-12-31

return_five_firms_garch <-

fread("dsf_new.csv", select = c("DATE", "PERMNO", "RET")) %>%
  clean_names() %>%
  filter((date >= 20000101 & date <= 20101231) & permno %in% garch_coef_five_firms$permno) %>%
  mutate(ret = as.numeric(ret)) %>%
  na.omit()


```


```{r}

# Add initial variance to each of the 5 firms

return_five_firms_garch <-

left_join(return_five_firms_garch[, .SD[1], by = permno], initial_variance[initial_variance$permno %in% garch_coef_five_firms$permno, ], by = c("permno" = "permno")) %>%
  left_join(return_five_firms_garch, ., by = c("permno" = "permno", "date" = "date", "ret" = "ret"))

```


```{r}

return_five_firms_garch <-
  left_join(return_five_firms_garch, garch_coef_five_firms, by = c("permno" = "permno"))

```


```{r}

# Apply the GARCH recursive formula to calculate variance according to the variance of previous day

for (i in 2:nrow(return_five_firms_garch))
{
   return_five_firms_garch$variance[i] = if_else (is.na(return_five_firms_garch$variance[i]), return_five_firms_garch$omega[i] +  return_five_firms_garch$beta[i] * return_five_firms_garch$variance[i-1] + return_five_firms_garch$alpha[i] * (return_five_firms_garch$ret[i-1])^2,
                                 return_five_firms_garch$variance[i])
}

```

Note: The variances used to estimate GARCH parameters are generated by calculating historical variance of rolling 25-day window from 2010 to 2019. However, for stock whose permno is 83664, it had less than 25 trading days in 2010 and ceased to exist. Therefore, there are no historical variances that can be used to estimate GARCH parameters for this stock. Unfortunately, it is one of the five stocks selected by my random seed.

Therefore, the following part only plots 4 stocks, instead of 5.

```{r}

# Plot the time series of variance generated by GARCH(1, 1) for each of the 5 firms

return_five_firms_garch %>%
  mutate(date = ymd(date)) %>%
  group_by(date, permno) %>%
  ggplot(aes(x = date, y = variance)) +
  geom_line() +
  facet_wrap(~ permno, scales = "free", nrow = 2, ncol = 2) +
  labs(title = "Variance by GARCH(1, 1)") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = .5))

```








