---
title: "MGT6090 Assignment 3"
author: "Yuguang Shen"
date: "September 10, 2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

# Install and load packages

This code block installs and loads necessary packages for this project.

```{r}
# install.packages("tidyverse")
# install.packages("tidyquant")
# install.packages("janitor")
# install.packages("timetk")
# install.packages("corrr")
# install.packages("patchwork")
# install.packages("corrplot")
# install.packages("data.table")




library(tidyverse)
library(tidyquant)
library(janitor)
library(lubridate)
library(timetk)
library(readxl)
library(corrr)
library(patchwork)
library(corrplot)


```


# Macro economic indicators

Import macro economic indicators from FRED and generate geom for each indicator


## FRED Unemployment Rate (Monthly)

```{r}
# When importing FRED data, set a "from" time early enough to cover the entire period of our interest
# In this project, 1985 is early enough
unemployment <-
  "UNRATE" %>%
  tq_get(get = "economic.data", from = "1985-01-01") %>%
  rename("fred_code" = "symbol", "unemployment_rate" = "price") %>%
  select(-fred_code)

unemployment_layer <-
  geom_line(data = unemployment, aes(x = date, y = unemployment_rate ), color = "red") 

```


## FRED Real GDP Pct Change (Quarterly)

```{r}
real_gdp <-
  "A191RL1Q225SBEA" %>%
  tq_get(get = "economic.data", from = "1985-01-01") %>%
  rename("fred_code" = "symbol", "real_gdp_change" = "price") %>%
  select(-fred_code)

real_gdp_layer <-

  geom_line(data = real_gdp, aes(x = date, y = real_gdp_change ), color = "blue") 

```


## FRED Effective Fedral Funds Rate (Monthly)

```{r}
fed_rate <-
  "FEDFUNDS" %>%
  tq_get(get = "economic.data", from = "1985-01-01") %>%
  rename("fred_code" = "symbol", "fed_fund_rate" = "price") %>%
  select(-fred_code)

fed_rate_layer <-
  geom_line(data = fed_rate, aes(x = date, y = fed_fund_rate ), color = "orange")


```




# Useful Functions

Create some functions to automate data analysis and reporting

## calculate_stats(my_df, "col_1", "col_2")

This function calculates the descriptive statistics for certain columns in a dataset.

```{r}
calculate_stats <- function(my_df, col_1, col_2){
  
  stats_result <-
  my_df %>%
    summarise(across(col_1:col_2, 
                   list(mean = ~mean(., na.rm = TRUE), 
                        P25 = ~quantile(.,0.25, na.rm = TRUE),
                        P50 = ~quantile(.,0.5, na.rm = TRUE),
                        P75 = ~quantile(.,0.75, na.rm = TRUE),
                        sd = ~sd(., na.rm = TRUE)
                        ))) 
  
  return (stats_result)
}

```


## generate_plot(my_df)

This function draws plots together with macro economic indicators for a dataset.

```{r}
generate_plot <- function(my_df){
  
  plot_list <- list()
  
  names <- 
    my_df %>%
    select(-date) %>%
    colnames()
  
  # Created unemployment plot
  unemployment_plot <-
    ggplot() + 
    unemployment_layer +
    labs(title = "Unemployment Rate",
        y = "Unemployment Rate (%)",
        x = "") +
  scale_x_date( date_labels = "%Y", 
               limits = c(min(my_df$date), max(my_df$date))) +
  theme(axis.text.x=element_text(angle=60, hjust=1))
  
  # Create Real_GDP plot
  real_gdp_plot <-
    ggplot() +
    real_gdp_layer +
     labs(title = "Real GDP Percent Change",
        y = "Real GPD Change (%)",
        x = "") +
   scale_x_date( date_labels = "%Y", 
                limits = c(min(my_df$date), max(my_df$date))) +
   scale_y_continuous(breaks = seq(-35, 35, by = 5)) +
   theme(axis.text.x=element_text(angle=60, hjust=1)) +
   geom_hline(yintercept = 0)
  
  # Create Effective Fed Funds Rate plot
  fed_rate_plot <-
    ggplot() + 
    fed_rate_layer + 
      labs(title = "Effective Federal Funds Rate",
       y = "Fed Funds Rate (%)",
       x = "") +
  scale_x_date( date_labels = "%Y",
                limits = c(min(my_df$date), max(my_df$date))) +
  theme(axis.text.x=element_text(angle=60, hjust=1)) 
  
  # Plot each column of my_df with three macro economic indicators and save the plots to a list
  
  for (i in names) {
  
  temp_plot <-
    my_df %>%
    ggplot(aes_string(x = my_df$date, y = i)) + 
    geom_line() + 
    labs(title = i,
       y = "Volume (Billions $)",
       x = "") +
    scale_x_date( date_labels = "%Y") +
    theme(axis.text.x=element_text(angle=60, hjust=1)) 
  
  output_plot <-  
    (unemployment_plot | real_gdp_plot | fed_rate_plot) / 
    (temp_plot | temp_plot | temp_plot)

  plot_list[[i]] <- output_plot

  }
  
  return (plot_list)
  
}

```


## get_correlation(my_df, "title_for_output")

This function calculates and visualizes the correlation among columns of a dataset.

```{r}
get_correlation <- function(my_df, title)
{
  cor_heatmap <-
  my_df %>%
  select(-date) %>%
  cor(use="pairwise.complete.obs") %>%
  corrplot(method = "number", title = title, mar=c(0,0,1,0))
  
  return (cor_heatmap)
  
}

```


# Data import and cleaning

Import and clean data

## US Treasury Trading

```{r}

treasury_trading <-
  
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/ta-us-treasury-trading-volume-sifma.xls", sheet = "Monthly", guess_max = 1000, skip = 5) %>%
  data.table::setnames(old = colnames(.), new = c("date", "t_bill", "tiis", "frn", "coupon_<2", "coupon_2-3", "coupon_3-6", "coupon_6-7",                "coupon_7-11", "coupon_>11", "total")) %>%
  clean_names() %>%
  mutate(date_new = my(date)) %>%
  mutate(date = as.numeric(date)) %>%
  mutate(date = as_date(date, origin = "1899-12-30")) %>%
  mutate(date_new = ceiling_date(date_new, unit = "month") - 1) %>%
  mutate(date = case_when(is.na(date) & !is.na(date_new) ~ date_new,
                                 TRUE ~ date)
                ) %>%
  mutate(across(-date, as.numeric)) %>%
  select(-date_new) %>%
  filter(!is.na(date)) 

```











## US Equity Capital Formation and Trading
```{r}
equity_cap_formation <-
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Equities-and-Related-Statistics-SIFMA.xlsx", sheet = "Capital Formation", guess_max = 1000, skip = 8, range = "A9:F79") %>%
  rename("date" = "...1", "ipo" = "IPOs") %>%
  clean_names() %>%
  filter(!is.na(date)) %>%
  filter(date != "2020" & date != "2019") %>%
  mutate(date_new = make_date(date, 12, 31)) %>%
  filter(!is.na(date_new) ) %>%
  mutate(date = case_when(year(date_new) < 2021 ~ date_new,
                           TRUE ~ as_date(as.numeric(date), origin = "1899-12-30"))) %>%
  select(-date_new)

```

```{r}
equity_trading <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Equities-and-Related-Statistics-SIFMA.xlsx", sheet = "ADV $", guess_max = 1000, skip = 8, range = "A9:L71") %>%
  select(-...5) %>%
  select(-...11) %>%
  rename("date" = "...1") %>%
  clean_names() %>%
  filter(!is.na(market)) %>%
  filter(date != "2020" & date != "2019" & date != "2008") %>%
  mutate(date_new = make_date(date, 12, 31)) %>%
  filter(!is.na(date_new) ) %>%
  mutate(date = case_when(year(date_new) < 2021 ~ date_new,
                           TRUE ~ as_date(as.numeric(date), origin = "1899-12-30"))) %>%
  select(-date_new) %>%
  mutate(across(tape_a:market, as.numeric))
  
```


## US Fixed Income Trading
```{r}
fix_income_trading <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Fixed-Income-Securities-Statistics-SIFMA.xlsx", sheet = "Trading Volume", guess_max = 1000, skip = 7, range = "A8:I81") %>%
  rename("date" = "...1") %>%
  clean_names() %>%
  mutate(across(everything(), as.numeric)) %>%
  filter(date != 2019 & date != 2020 & !is.na(date)) %>%
  mutate(date_new = make_date(date, 12, 31)) %>%
  mutate(date = case_when(year(date_new) < 2021 ~ date_new,
                            TRUE ~ as_date(date, origin = "1899-12-30"))) %>%
  select(-date_new) %>%
  rename("fed_agen_securities" = "federal_agency_securities")

```



## US SF Trading Daily and Monthly
```{r}
sf_trading_daily <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/sf-us-sf-trading-volume-sifma.xls", sheet = "TRACE - Daily", guess_max = 5000, range = "A6:R2346", .name_repair = "unique") %>%
  select(-...6) %>%
  select(-...17) %>%
  rename("total_agency" = "Total...5", "total_non_agency" = "Total...16") %>%
  clean_names() %>%
  mutate(date = ymd(date)) %>%
  mutate(month = ceiling_date(date, "month") - 1) %>%
  relocate(month, .after = date)

# Aggregate daily data to monthly
sf_trading_monthly <-
  sf_trading_daily %>%
  group_by(month) %>%
  summarise(across(cmo:grand_total, 
                   list(m = ~mean(., na.rm = TRUE)))) %>%
  rename("date" = "month") 
  
```

## US Agency Trading
```{r}
agency_trading <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/ta-us-agency-trading-volume-sifma.xls", sheet = "Trading Volume", guess_max = 5000, range = "A10:F136") %>%
  rename("date" = "...1") %>%
  mutate(date = ymd(date)) %>%
  clean_names() %>%
  rename("other" = "other2") %>%
  mutate(date = ceiling_date(date, "month") - 1)

```

## US Corporate Bond Trading
```{r}
corp_bond_trading <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/corporate-us-corporate-trading-volume-sifma.xls", sheet = "TRACE", guess_max = 5000, range = "A10:N198") %>%
  select(-...5) %>%
  select(-...9) %>%
  select(-...13) %>%
  data.table::setnames(old = colnames(.), new = c("date", "pt_ig", "pt_hy", "pt_total", "ig_144a", "hy_144a", "total_144a", "nc_ig", "nc_hy", "nc_total", "c_total")) %>%
  mutate(date = ymd(date)) %>%
  mutate(date = ceiling_date(date, "month") - 1)

```

## US Treasury Issuance, Outstanding, and Interest Rates
```{r}
# Issuance
treasury_issuance <-
      read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Treasury-Securities-Statistics-SIFMA.xlsx", sheet = "Issuance Net", guess_max = 5000, range = "A9:P30") %>%
  select(-...5) %>%
  select(-...9) %>%
  select(-...13) %>%
  data.table::setnames(old = colnames(.), new = c("date", "bill_gi", "bill_gr", "bill_net", "notes_gi", "notes_gr", "notes_net", "bond_gi", "bond_gr", "bond_net", "total_gi", "total_gr", "total_net")) %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "month") - 1)

# Outstanding
treasury_outstand <-
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Treasury-Securities-Statistics-SIFMA.xlsx", sheet = "Outstanding", guess_max = 5000, range = "A8:G39") %>%
  rename("date" = "...1") %>%
  clean_names() %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1)


# Interest Rates
treasury_rates <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Treasury-Securities-Statistics-SIFMA.xlsx", sheet = "Yield Curve Rates", guess_max = 5000, range = "A9:D40") %>%
  rename("date" = "...1") %>%
  clean_names() %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1) %>%
  rename("3_month_bills" = "x3_month_bills", "10_year_notes" = "x10_year_notes") %>%
  rename("bills_3_month" = "3_month_bills") %>%
  rename("notes_10_year" = "10_year_notes") 

```
## US MBS Issuance and Outstanding
```{r}
# MBS Issuance
mbs_issuance <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Mortgage-Backed-Securities-Statistics-SIFMA.xlsx", sheet = "MBS Issuance", guess_max = 5000, range = "A19:J44") %>%
  select(-...4) %>%
  select(-...7) %>%
  clean_names() %>%
  data.table::setnames(old = colnames(.), new = c("date", "a_mbs", "a_cmo", "na_cmbs", "na_rmbs", "a_total", "na_total", "total")) %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1)


# MBS Outstanding
mbs_outstand <-
      read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Mortgage-Backed-Securities-Statistics-SIFMA.xlsx", sheet = "MBS Outstanding", guess_max = 5000, range = "A18:J37") %>%
  select(-...4) %>%
  select(-...7) %>%
  clean_names() %>%
  data.table::setnames(old = colnames(.), new = c("date", "a_mbs", "a_cmo", "na_cmbs", "na_rmbs", "a_total", "na_total", "total")) %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1)

```
## US ABS Issuance and Outstanding
```{r}
# ABS Issuance
abs_issuance <-
   read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Asset-Backed-Securities-Statistics-SIFMA.xlsx", sheet = "ABS Issuance", guess_max = 5000, range = "A11:H47") %>%
  clean_names() %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1)

# ABS Outstanding
abs_outstand <-
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Asset-Backed-Securities-Statistics-SIFMA.xlsx", sheet = "ABS Outstanding", guess_max = 5000,  range = "A14:H50") %>%
  clean_names() %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1)

```
## US Fix Income Issuance and Outstanding
```{r}
# Fix Income Issuance
fix_income_issuance <-
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Fixed-Income-Securities-Statistics-SIFMA.xlsx", sheet = "Issuance", guess_max = 1000, range = "A8:H33") %>%
  rename("date" = "...1") %>%
  clean_names() %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1) %>%
  rename("fed_agen_securities" = "federal_agency_securities")


# Fix Income Outstanding
fix_income_outstand <-
    read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Fixed-Income-Securities-Statistics-SIFMA.xlsx", sheet = "Outstanding", guess_max = 1000, range = "A8:I49") %>%
  rename("date" = "...1") %>%
  clean_names() %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1) %>%
  mutate(asset_backed = as.numeric(asset_backed)) %>%
  rename("fed_agen_securities" = "federal_agency_securities")

```
## US ABCP and CP Outstanding (Money Market Instrument)
```{r}

mm_outstand <-
   read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Money-Market-Instruments-Statistics-SIFMA.xlsx", sheet = "Outstanding MM Instruments", guess_max = 1000, range = "A9:J34") %>%
  select(-...5) %>%
  clean_names() %>%
  rename("date" = "x1") %>%
  select(-commercial_paper) %>%
  data.table::setnames(old = c("total_4", "non_financial", "financial", "abcp", "other", "total_10"),
                       new = c("total", "cp_non_fin", "cp_fin", "cp_abcp", "cp_other", "cp_total")) %>%
  relocate(bankers_acceptance, .after = cp_total) %>%
  relocate(total, .after = bankers_acceptance) %>%
  mutate(across(-date, as.numeric)) %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1)

```
## US Municipal Issuance
```{r}
muni_issuance <-
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Municipal-Bonds-Statistics-SIFMA.xlsx", sheet = "Issuance Total", guess_max = 1000, range = "A9:L34") %>%
  select(-...4) %>%
  select(-...8) %>%
  select(-...11) %>%
  rename("date" = "...1") %>%
  clean_names() %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1) %>%
  rename("pvt_plc" = "private_placement")


```
## US Corporate Bond Issuance
```{r}
corp_bond_issuance <-
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/US-Corporate-Bonds-Statistics-SIFMA.xlsx", sheet = "Issuance", guess_max = 5000, range = "A9:N34") %>%
  select(-...5) %>%
  select(-...8) %>%
  select(-...11) %>%
  select(-...13) %>%
  clean_names() %>%
  data.table::setnames(old = c("x1", "total", "x12", "x14"), 
                       new = c("date", "ig_hy_comb", "convertable", "total")) %>%
  mutate(date = make_date(date)) %>%
  mutate(date = ceiling_date(date, "year") - 1) %>%
  rename("ig" = "investment_grade", "hy" = "high_yield")

```
## Crypto Trading
```{r}
data_dir <- "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Crypto"

# Create a list for all data file names
data_files_list <- list.files(path = data_dir, pattern = "*.csv", full.names = TRUE)
file_names <-list.files(path = data_dir, pattern = "*.csv", full.names = FALSE)

crypto_trading <- map_dfr(data_files_list, read_csv, .id = "ticker")

# Assign ticker to each crypto
for (i in 1:10){
  
  crypto_trading <-
    crypto_trading %>%
    mutate( ticker = case_when(ticker == i ~ sub("\\-.*", "", file_names[i]),
                               TRUE ~ ticker))
}


crypto_trading %>%
  data.table::setnames(old = c("snapped_at", "market_cap", "total_volume"), 
                       new = c("date", "market_cap_bil", "total_volume_bil"))

crypto_trading <-
  crypto_trading %>%
  mutate(date = ymd_hms(date)) %>% 
  mutate(date = as.Date(date)) %>%
  mutate(market_cap_bil = market_cap_bil / 1000000000) %>%
  mutate(total_volume_bil = total_volume_bil / 1000000000)

```
## US Repo

```{r}

# Triparty Repo

triparty_repo <-
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/Funding-US-Repo-SIFMA.xlsx", sheet = "Triparty Repo", guess_max = 5000, skip = 2)

# Extract the collateral volume data into a new dataset. Collateral volume is equivalent to trading volume, because every repo trade must come with a collateral with at least the same value (usually a little bit higher).

triparty_repo_collateral <-
  triparty_repo %>%
  slice(2:45) %>%
  mutate(...1 = case_when(...1 == "Fedwire-eligible" ~ "fedwire",
                          ...1 == "Non Fedwire-eligible" ~ "non_fedwire",
                          ...1 == "Both Fedwire-eligible and non-eligible" ~ "both",
                          TRUE ~ ...1)) %>%
  filter(!is.na(...2)) %>%
  fill(...1, .direction = "down") %>%
  unite("collateral_type", ...1:...2, sep = "_", remove = TRUE) %>%
  data.table::transpose(keep.names = "date", make.names = "collateral_type") %>%
  clean_names() %>%
  mutate(across(everything(), as.numeric)) %>%
  mutate(date = as_date(date, origin = "1899-12-30"))

```

```{r}

# GCF Repo

gcf_repo <- 
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/Funding-US-Repo-SIFMA.xlsx", sheet = "GCF Repo", guess_max = 5000, skip = 3) %>%
  clean_names() %>%
  select(x1, total_par_amount_millions, x7, x8) %>%
    mutate(across(everything(), as.numeric)) %>%
  data.table::setnames(old = colnames(.), new = c("date", "treasury", "agency", "mbs")) %>%
  filter(!is.na(date)) %>%
  filter(date > 2019) %>%
  mutate(date = as_date(date, origin = "1899-12-30"))

```

```{r}

# Primary Dealer Repo

primary_dealer_repo <- 
  read_excel(path = "C:/_Ga Tech/MS QCF/2021 Fall/MGT6090/Assignment 3/Data/Funding-US-Repo-SIFMA.xlsx", sheet = "PrimaryDealer", guess_max = 5000, range = "A5:K194") %>%
  select(-c(...6, ...10)) %>%
  data.table::setnames(old = colnames(.), new = 
                         c("year", "q", "repo_overnight", "repo_term", "repo_total",
                           "r_repo_overnight", "r_repo_term", "r_repo_total", "total")) %>%
  filter(!(is.na(year) & is.na(q))) %>%
  fill(year, .direction = "down") %>%
  unite("date", year:q, sep = "/", remove = TRUE, na.rm = TRUE) %>%
  mutate(date_num = as.numeric(date)) %>% 
  filter(is.na(date_num)) %>%
  select(-date_num)

```

# Data analysis and visualization

Analyze the data and visualize the results

## US Treasury Trading Data

```{r}

calculate_stats(treasury_trading, "t_bill", "total")

generate_plot(treasury_trading)

get_correlation(treasury_trading, "Correlation within US Treasury Trading")

```

## US Equity Trading  and Capital Formation Data

```{r}

# Equity Trading

calculate_stats(equity_trading, "tape_a", "market")

generate_plot(equity_trading)

get_correlation(equity_trading, "Correlation within US Equity Trading")

# Equity Capital Formation

calculate_stats(equity_cap_formation, "ipo", "total_equity")

generate_plot(equity_cap_formation)

get_correlation(equity_cap_formation, "Correlation within US Equity Cap Formation")

```

## US Fixed Income Trading Data

```{r}

calculate_stats(fix_income_trading, "municipal", "total")

generate_plot(fix_income_trading)

get_correlation(fix_income_trading, "Correlation within Fix Income Trading")

```

## US SF Trading Data, Monthly

```{r}

calculate_stats(sf_trading_monthly, "cmo_m", "grand_total_m")

generate_plot(sf_trading_monthly)

get_correlation(sf_trading_monthly, "Correlation within SF Trading")

```

## US Agency Trading Data

```{r}

calculate_stats(agency_trading, "fannie_mae", "total")

generate_plot(agency_trading)

get_correlation(agency_trading, "Correlation within Agency Trading")

```

## US Corporate Bond Trading Data

```{r}

calculate_stats(corp_bond_trading, "pt_ig", "c_total")

generate_plot(corp_bond_trading)

get_correlation(corp_bond_trading, "Correlation within Corporate Bond Trading")

```

## US Treasury Issuance, Outstanding and Interest Rate Data

```{r}
# Treasury Issuance

calculate_stats(treasury_issuance, "bill_gi", "total_net")

generate_plot(treasury_issuance)

get_correlation(treasury_issuance, "Correlation of Treasury Issuance")

# Treasury Outstanding

calculate_stats(treasury_outstand, "bills", "total")

generate_plot(treasury_outstand)

get_correlation(treasury_outstand, "Correlation of Treasury Outstanding")

# Treasury Interest Rates

calculate_stats(treasury_rates, "bills_3_month", "spread")

generate_plot(treasury_rates)

get_correlation(treasury_rates, "Correlation of Treasury Interest Rates")

```


## US MBS Issuance and Outstanding Data

```{r}

# MBS Issuance

calculate_stats(mbs_issuance, "a_mbs", "total")

generate_plot(mbs_issuance)

get_correlation(mbs_issuance, "Correlation of MBS Issuance")

# MBS Outstanding

calculate_stats(mbs_outstand, "a_mbs", "total")

generate_plot(mbs_outstand)

get_correlation(mbs_outstand, "Correlation of MBS Outstanding")

```

## US ABS Issuance and Outstanding Data

```{r}

# ABS Issuance

calculate_stats(abs_issuance, "auto", "total")

generate_plot(abs_issuance)

get_correlation(abs_issuance, "Correlation of ABS Issuance")

# ABS Outstanding

calculate_stats(abs_outstand, "automobile", "total")

generate_plot(abs_outstand)

get_correlation(abs_outstand, "Correlation of ABS Outstanding")

```

## US Fix Income Issuance and Outstanding Data

```{r}

# Fix Income Issuance

calculate_stats(fix_income_issuance, "municipal", "total")

generate_plot(fix_income_issuance)

get_correlation(fix_income_issuance, "Correlation of Fix Income Issuance")

# Fix Income Outstanding

calculate_stats(fix_income_outstand, "municipal", "total")

generate_plot(fix_income_outstand)

get_correlation(fix_income_outstand, "Correlation of Fix Income Outstanding")


```

## US Money Market Insrument Outstanding

```{r}

calculate_stats(mm_outstand, "cp_non_fin", "total")

generate_plot(mm_outstand)

get_correlation(mm_outstand, "Correlation of Money Market Instrument Outstanding")

```

## US Municipal Issuance Data

```{r}

calculate_stats(muni_issuance, "go", "total")

generate_plot(muni_issuance)

get_correlation(muni_issuance, "Correlation of Municipal Issuance")

```

## US Repo

```{r}

# Triparty repo collateral

triparty_repo_collateral %>%
  select(date, fedwire_subtotal, non_fedwire_subtotal, both_total) %>%
  calculate_stats("fedwire_subtotal", "both_total")

triparty_repo_collateral %>%
  select(date, fedwire_subtotal, non_fedwire_subtotal, both_total) %>%
  generate_plot()

triparty_repo_collateral %>%
  select(date, fedwire_subtotal, non_fedwire_subtotal, both_total) %>%
  get_correlation("Correlation of Fedwire and Non Fedwire collateral in Triparty Repo")

# GCF Repo

calculate_stats(gcf_repo, "treasury", "mbs")

generate_plot(gcf_repo)

get_correlation(gcf_repo, "Correlation of different collaterals in GCF Repo")



```
## US Corporate Bond Issuance Data

```{r}

calculate_stats(corp_bond_issuance, "ig", "total")

generate_plot(corp_bond_issuance)

get_correlation(corp_bond_issuance, "Correlation of Corporate Bond Issuance")

```

## Crypto Trading Data

```{r}

# Extract only trading volume from the original data set

crypto_volume <-
  crypto_trading %>%
  select(-price) %>%
  select(-market_cap_bil)

```


```{r}
# Calculate descriptive statistics

crypto_volume %>%
  group_by(ticker) %>%
  calculate_stats("total_volume_bil", "total_volume_bil")

```


Plot time series of volume for each crypto

```{r}
# ada

ada_volume <-
  crypto_volume %>%
  filter(ticker == "ada") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(ada_volume)

```


```{r}
# bnb

bnb_volume <-
  crypto_volume %>%
  filter(ticker == "bnb") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(bnb_volume)

```


```{r}
# btc

btc_volume <-
  crypto_volume %>%
  filter(ticker == "btc") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(btc_volume)

```


```{r}
# doge

doge_volume <-
  crypto_volume %>%
  filter(ticker == "doge") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(doge_volume)

```


```{r}
# dot

dot_volume <-
  crypto_volume %>%
  filter(ticker == "dot") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(dot_volume)

```


```{r}
# eth

eth_volume <-
  crypto_volume %>%
  filter(ticker == "eth") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(eth_volume)

```


```{r}
# sol

sol_volume <-
  crypto_volume %>%
  filter(ticker == "sol") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(sol_volume)

```


```{r}
# usdc

usdc_volume <-
  crypto_volume %>%
  filter(ticker == "usdc") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(usdc_volume)

```


```{r}
# usdt

usdt_volume <-
  crypto_volume %>%
  filter(ticker == "usdt") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(usdt_volume)

```


```{r}
# xrp

xrp_volume <-
  crypto_volume %>%
  filter(ticker == "xrp") %>%
  pivot_wider(names_from = ticker, values_from = total_volume_bil, values_fill = NA)

generate_plot(xrp_volume)

```


Merge individual crypto trading data together and calculate correlation.

```{r}

crypto_merged <-
Reduce(function(...) merge(..., all=TRUE), list(ada_volume, bnb_volume, btc_volume, doge_volume, 
                                                dot_volume, eth_volume, sol_volume, usdc_volume,
                                                usdt_volume, xrp_volume))

get_correlation(crypto_merged, "Correlation of Top 10 Market Cap Crypto")

```





## Cross Market Correlation

```{r}

treasury_total <-
  treasury_trading %>%
  select(date, total) %>%
  rename("treasury_total" = "total")

equity_total <-
  equity_trading %>%
  select(date, market) %>%
  rename("equity_total" = "market")

fix_income_total <-
  fix_income_trading %>%
  select(date, total) %>%
  rename("fi_total" = "total")

sf_total <-
  sf_trading_monthly %>%
  select(date, grand_total_m) %>%
  rename("sf_total" = "grand_total_m")

agency_total <-
  agency_trading %>%
  select(date, total) %>%
  rename("agency_total" = "total")

corp_bond_total <-
  corp_bond_trading %>%
  mutate(corp_bond_total = select(., pt_total,total_144a,nc_total,c_total) %>% rowSums(na.rm = TRUE)) %>%
  select(date, corp_bond_total)

crypto_total <-
  crypto_merged %>%
  mutate(crypto_total = select(., -date) %>% rowSums(na.rm = TRUE)) %>%
  select(date, crypto_total)
  

cross_market_total <-
  Reduce(function(...) merge(..., all=TRUE), list(treasury_total, equity_total, fix_income_total,
                                                  sf_total, agency_total, corp_bond_total,
                                                  crypto_total))


get_correlation(cross_market_total, "Cross Market Correlation of Trading Volume")


```









# Possible way to double Y axis.
Limitation: Second Y axis is the same scale with the primary.

```{r}
  # plot_data <-
  #   
  # my_df %>%
  # ggplot() +
  # geom_boxplot(aes_string(x = my_df$datadate, y = col_1, group = my_df$fyear)) + 
  #  geom_line(data = kc_fin_stress, aes(x = date, y = kcfsi), color = "blue") +
  #  scale_y_continuous(sec.axis = sec_axis(~., name = "kcfsi")) +
  # 
  # labs(title = paste(col_1, " and Kansas City Financial Stress Index over year"),
  #      x = "year")
  # theme_classic()
  # 
  # 
  # 
  # return (plot_result)

```