---
title: 'MGT 6090 Assignment 5 Part 3: DSF descriptive stats'
author: "Yuguang Shen"
date: "October 1, 2021"
output:
  pdf_document:
    fig_height: 5.5
    fig_width: 7
  word_document: default
  html_document: default
---

```{r, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidyquant)
library(lubridate)
library(janitor)
library(corrplot)
library(data.table)
library(patchwork)
library(gt)
library(knitr)
library(RColorBrewer)
library(data.table)

```

# Useful Functions

```{r}

# Function to get n, mean, sd, ect

get_stats <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_n" = ~n(),
                        "_mean" = ~mean(., na.rm = TRUE), 
                        "_sd" = ~sd(., na.rm = TRUE),
                        "_skew" = ~skewness(., na.rm = TRUE),
                        "_kurt" = ~kurtosis(., na.rm = TRUE),
                        "_min" = ~min(., na.rm = TRUE),
                        "_max" = ~max(., na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "n, mean, sd, skewness, kurtosis, min, max") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = mean:max, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

# Function to get percentiles

get_percentiles <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_P1" = ~quantile(.,0.01, na.rm = TRUE),
                        "_P5" = ~quantile(.,0.05, na.rm = TRUE),
                        "_P25" = ~quantile(.,0.25, na.rm = TRUE),
                        "_P50" = ~quantile(.,0.5, na.rm = TRUE),
                        "_P75" = ~quantile(.,0.75, na.rm = TRUE),
                        "_P95" = ~quantile(.,0.95, na.rm = TRUE),
                        "_P99" = ~quantile(.,0.99, na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "percentiles") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = P1:P99, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

```


# Load DSF dataset

```{r}

# data.table package is good for large dataset

dsf <- 
  fread("dsf_new.csv", select = c("PERMNO", "DATE", "SHRCD",  "PRC", "VOL", 
                                  "OPENPRC", "ASKHI", "BIDLO", "BID", "ASK",
                                  "SHROUT", "RET", "VWRETD")) %>%
  filter(SHRCD %in% c(10, 11)) %>%
  select(-SHRCD) %>% 
  clean_names()

```

# Add features

```{r, message=FALSE, warning=FALSE}

dsf <-
  
dsf %>%
  mutate(date = ymd(date),
         prc = abs(prc),
         ret = as.numeric(ret),
         bid_ask_spread = ask - bid,
         price_range = askhi - bidlo,
         close_open = prc - openprc,
         mkt_cap = prc * shrout * 1000 / 1000000,
         date_month = ceiling_date(date, "months") - 1)

```

# Descriptive Statistics for Daily Return, Daily Closing Price, Daily Bid-Ask Spread, Volume, Price Range, and Close-Open

```{r, message=FALSE, warning=FALSE}

dsf %>%
  get_stats(NULL, c("ret", "prc", "bid_ask_spread", "vol", "price_range", "close_open"))

dsf %>%
  get_percentiles(NULL, c("ret", "prc", "bid_ask_spread", "vol", "price_range", "close_open"))

```

# Plot statistics for Daily Price Range, Daily Close-Open, and Daily Return

## Generate statistics tables for each variable

```{r, message=FALSE, warning=FALSE}

# Create table for Daily Price Range

price_range_stats_table <-
  dsf %>%
  select(date, price_range) %>%
  get_stats("date", "price_range")

price_range_percentile_table <-
  dsf %>%
  select(date, price_range) %>%
  get_percentiles("date", "price_range")
  
```


```{r, message=FALSE, warning=FALSE}

# Create table for Daily Close-Open

close_open_stats_table <-
  dsf %>%
  select(date, close_open) %>%
  get_stats("date", "close_open")

close_open_percentile_table <-
  dsf %>%
  select(date, close_open) %>%
  get_percentiles("date", "close_open")

```


```{r, message=FALSE, warning=FALSE}

# Create table for Daily Return

ret_stats_table <-
  dsf %>%
  select(date, ret) %>%
  get_stats("date", "ret")

ret_percentile_table <-
  dsf %>%
  select(date, ret) %>%
  get_percentiles("date", "ret")

```


## Plot certain stats over time for each variable

```{r, message=FALSE, warning=FALSE}

# Plot mean, sd, 25th, 75th for Daily Price Range over time

price_range_stats_table$`_data` %>%
  select(date, mean, sd) %>%
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) +
  geom_line(lwd = 0.1) +
  labs(title = "Daily Mean and Sd of Price Range")


price_range_percentile_table$`_data` %>%
  select(date, P25, P75) %>%
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) +
  geom_line(lwd = 0.1) +
  labs(title = "Daily 25th and 75th Percentile of Price Range")

```


```{r, message=FALSE, warning=FALSE}

# Plot mean, sd, 25th, 75th for Daily Close-Open over time

close_open_stats_table$`_data` %>%
  select(date, mean, sd) %>%
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) +
  geom_line(lwd = 0.1) +
  labs(title = "Daily Mean and Sd of Close-Open")


close_open_percentile_table$`_data` %>%
  select(date, P25, P75) %>%
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) +
  geom_line(lwd = 0.1) +
  labs(title = "Daily 25th and 75th Percentile of Close-Open")

```


```{r, message=FALSE, warning=FALSE}

# Plot mean, sd, 25th, 75th for Daily Return over time

ret_stats_table$`_data` %>%
  select(date, mean, sd) %>%
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) +
  geom_line(lwd = 0.1) +
  labs(title = "Daily Mean and Sd of Return")


ret_percentile_table$`_data` %>%
  select(date, P25, P75) %>%
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) +
  geom_line(lwd = 0.1) +
  labs(title = "Daily 25th and 75th Percentile of Return")

```

# Save dsf file to be used in next part

```{r, message=FALSE, warning=FALSE}

# Trim down dsf data for next step

# dsf <-
#   dsf %>%
#   select(permno, date, date_month, ret, mkt_cap, vwretd)

# Save the trimed dsf file

# fwrite(dsf, "dsf_ipo.csv")

```













