---
title: 'MGT 6090 Assignment 5 Part 4: IPO'
author: "Yuguang Shen"
date: "October 2, 2021"
output:
  pdf_document: default
  html_document: default
---


```{r, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidyquant)
library(lubridate)
library(janitor)
library(corrplot)
library(data.table)
library(patchwork)
library(gt)
library(knitr)
library(RColorBrewer)
library(data.table)

```


# Useful Functions

```{r}

# Function to get n, mean, sd, ect

get_stats <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_n" = ~n(),
                        "_mean" = ~mean(., na.rm = TRUE), 
                        "_sd" = ~sd(., na.rm = TRUE),
                        "_skew" = ~skewness(., na.rm = TRUE),
                        "_kurt" = ~kurtosis(., na.rm = TRUE),
                        "_min" = ~min(., na.rm = TRUE),
                        "_max" = ~max(., na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "n, mean, sd, skewness, kurtosis, min, max") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = mean:max, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

# Function to get percentiles

get_percentiles <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_P1" = ~quantile(.,0.01, na.rm = TRUE),
                        "_P5" = ~quantile(.,0.05, na.rm = TRUE),
                        "_P25" = ~quantile(.,0.25, na.rm = TRUE),
                        "_P50" = ~quantile(.,0.5, na.rm = TRUE),
                        "_P75" = ~quantile(.,0.75, na.rm = TRUE),
                        "_P95" = ~quantile(.,0.95, na.rm = TRUE),
                        "_P99" = ~quantile(.,0.99, na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "percentiles") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = P1:P99, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  return (stats_table)
  
}

```







# IPO Analysis

## Load dsf dataset generated from previous part and create a dataset for IPO

```{r}

ipo <- 
  fread("dsf_ipo.csv") %>%
  filter(!is.na(ret))

```

## Add more features

```{r}

# ipo_counter will be used to calculate IPO numbers in each month

find_ipo_start <-
  ipo[, .SD[1], by = permno] %>%
  mutate(ipo_counter = 1) %>%
  select(permno, date, ipo_counter)

```


```{r, message=FALSE, warning=FALSE}

# Join with original ipo dataset. 

ipo <-
  
 left_join(ipo, find_ipo_start, by = c("permno" = "permno", "date" = "date"))

# Drop find_ipo_start to save memory

rm(find_ipo_start)
gc()

```


```{r}

# Add column for Excess Return over Market

ipo <-

ipo %>%
  mutate(ret_mkt = ret - vwretd)

```


## Monthly number of IPOs and Market Return

```{r, message=FALSE, warning=FALSE}

# Create a dataset for monthly number IPOs and average IPO size

monthly_ipo <-
  
ipo %>%
  group_by(date_month) %>%
  summarise(n_ipo = sum(ipo_counter, na.rm = TRUE),
            mean_mktcap = mean(mkt_cap, na.rm = TRUE))

monthly_ipo <-
  monthly_ipo %>%
  mutate(date_month = ymd(date_month))

# Drop ipo_counter and mkt_cap columns to save memory

ipo <-
  ipo %>%
  select(-c(ipo_counter, mkt_cap))
gc()
  

# Create a dataset for monthly compounded market return in percentage

setDT(ipo)

monthly_mkt_ret <-

  ipo[, .SD[1], by = date] %>% 
  select(date_month, vwretd) %>% 
  group_by(date_month) %>%
  summarise(monthly_vwretd_pct = (prod(vwretd + 1, na.rm = TRUE) - 1) * 100)

monthly_mkt_ret <-
  monthly_mkt_ret %>%
  mutate(date_month = ymd(date_month))

# Combine the above two datasets 

monthly_ipo_and_mkt <-
  left_join(monthly_ipo, monthly_mkt_ret, by = "date_month")

```

Comments:

Regarding monthly number of IPOs, there are two data points that are abnormally high.

They are 1962-12 with "1965 IPOs" and 1972-12 with "2887 IPOs".

I did some google search and found the actual number of IPOs in 1962 and 1972 from a paper:

https://www.jstor.org/stable/3648214?seq=6#metadata_info_tab_contents

1962 whole year: 236 IPOs
1972 whole year: 448 IPOs

The possible explaination for these two outliers is :

1962-12 is actually the first month of this dataset. It just means that CRSP started recording these stocks, not meaning that they were all IPOs.

In 1984, CRSP added data from the NASDAQ markets, which dated from December 1972. Therefore, 1972-12 was just the starting time to track NASDAQ data, not meaning that there were 2887 IPOs.

The effects of these two outliers can also been seen in Assignment 5_Part 1, where the monthly number of stocks plot takes two almost vertical jumps at these two time points.

In the following part, I used the actual IPO number and divided by 12 to estimate the IPO number in those two months. In this way, the scale of monthly IPO number plot will look better. 

```{r, message=FALSE, warning=FALSE}

# Prepare CPI data

cpi <-
    "CPIAUCNS" %>%
  tq_get(get = "economic.data", from = "1913-01-01") %>%
  rename("fred_code" = "symbol", "monthly_cpi" = "price") %>%
  select(-fred_code) %>%
  mutate(date = ymd(date)) %>%
  mutate(date = ceiling_date(date, "months") - 1)

# Calculate average CPI for 2010

cpi_2010 <-
  cpi %>%
   filter(date >= "2010-01-31" & date <= "2010-12-31") %>%
   select(monthly_cpi) %>%
   colMeans()

# Recalculate CPI based on 2010 level

cpi <-
  cpi %>%
  mutate(monthly_cpi= monthly_cpi / cpi_2010 * 100)

monthly_ipo_and_mkt <-
  left_join(monthly_ipo_and_mkt, cpi, by = c("date_month" = "date"))

```

```{r, message=FALSE, warning=FALSE}

# Adjust Market Cap for CPI to 2010 Dollar

monthly_ipo_and_mkt <-
  
  monthly_ipo_and_mkt %>%
  mutate(mean_mktcap_as_2010 = mean_mktcap * 100 / monthly_cpi)

# Adjust number of IPOs for 1962-12-31 and 1972-12-31

monthly_ipo_and_mkt <-
  
  monthly_ipo_and_mkt %>%
  mutate(n_ipo = case_when(date_month == "1962-12-31" ~ 236 %/% 12,
                           date_month == "1972-12-31" ~ 448 %/% 12,
                           TRUE ~ n_ipo))

```


```{r, message=FALSE, warning=FALSE}

# Plot Monthly number of IPOs

monthly_ipo_and_mkt %>%

  ggplot(aes(x = date_month, y = monthly_vwretd_pct, fill = monthly_vwretd_pct >= 0)) +
  geom_col() +
  scale_fill_manual(values = c("red3", "green3"), guide = FALSE) +
  geom_line(data = monthly_ipo_and_mkt, aes(x = date_month, y = n_ipo / 5, group = 1), lwd = 0.1) +
  scale_y_continuous("Number of IPOs (x5)", sec.axis = sec_axis(trans=~.*1, name = "Market Return (%)") )+
  labs(title = "Monthly number of IPOs VS. Market Return",
       x = "Month")

```

## Monthly mean IPO size and Market Return

```{r, message=FALSE, warning=FALSE}

# Plot Monthly average IPO size

monthly_ipo_and_mkt %>%

  ggplot(aes(x = date_month, y = monthly_vwretd_pct, fill = monthly_vwretd_pct >= 0)) +
  geom_col() +
  scale_fill_manual(values = c("red3", "green3"), guide = FALSE) +
  geom_line(data = monthly_ipo_and_mkt, aes(x = date_month, y = mean_mktcap_as_2010 / 1000, group = 1), lwd = 0.1) +
  scale_y_continuous("Avg IPO Size (Billions, 2010 Dollar)", 
                     sec.axis = sec_axis(trans=~.*1, name = "Market Return (%)") )+
  labs(title = "Monthly Average IPO Size VS. Market Return",
       x = "Month")

```

## Monthly mean IPO First Day Return and Market Return

```{r, message=FALSE, warning=FALSE}

# Plot Monthly Average IPO First Day return

ipo[, .SD[1], by = permno] %>% 
  group_by(date_month) %>%
  summarise(mean_first_ret = mean(ret) * 100) %>%
  ggplot(aes(x = date_month, y = mean_first_ret)) + 
  geom_line(aes(group = 1, color = "1st day")) +
  geom_line(data = monthly_ipo_and_mkt, aes(x = date_month, y = monthly_vwretd_pct, group = 1, color = "mkt"), lwd = 0.1) +
  labs(title = "Monthly Average IPO First Day Return VS. Market Return",
       x = "Month",
       y = "Return (%)",
       colour = "Return")

```

## IPO's returns over different time horizon within 3 years of IPO

```{r}

rm(monthly_ipo_and_mkt)
rm(cpi)
rm(monthly_ipo)
rm(monthly_mkt_ret)
gc()

# Drop vwretd column to save memory

ipo <-
  ipo %>%
  select(-c(vwretd, date_month))

```

```{r}

# Find the first trading day for each stock

first_trading_date <-

ipo[, .SD[1], by = permno] %>%
  select(permno, date) %>%
  mutate(initial_date = date) %>%
  select(-date)

```

```{r}

# Join with ipo dataset

ipo <-

ipo %>%
  select(permno, date, ret, ret_mkt) %>%
  left_join(first_trading_date, by = c("permno" = "permno"))

rm(first_trading_date)
gc()

```

```{r}

# Construct first day return

setDT(ipo)

ipo_return <-
  
  ipo[date == initial_date, ][, ':='(first_day_ret = ret, first_day_excess_ret = ret_mkt)][,.(permno, first_day_ret, first_day_excess_ret)]  
  
```

```{r}

# Construct first month return and join with ipo_return

gc()


ipo_return <-

ipo[date <= add_with_rollback(initial_date, months(1)), ][,.(first_month_ret = prod(1 + ret, na.rm = TRUE) - 1,
            first_month_excess_ret = prod(1 + ret_mkt, na.rm = TRUE) - 1), by = permno] %>%
            left_join(ipo_return, temp, by = c("permno" = "permno"))

```

```{r}

# Construct first year return and join with ipo_return

gc()

ipo_return <-

ipo[date <= add_with_rollback(initial_date, months(12)), ][,.(first_year_ret = prod(1 + ret, na.rm = TRUE) - 1,
            first_year_excess_ret = prod(1 + ret_mkt, na.rm = TRUE) - 1), by = permno] %>%
            left_join(ipo_return, temp, by = c("permno" = "permno"))

```

```{r}

# Construct two year return and join with ipo_return

gc()

ipo_return <-

ipo[date <= add_with_rollback(initial_date, months(24)), ][,.(two_year_ret = prod(1 + ret, na.rm = TRUE) - 1,
            two_year_excess_ret = prod(1 + ret_mkt, na.rm = TRUE) - 1), by = permno] %>%
            left_join(ipo_return, temp, by = c("permno" = "permno"))


```

```{r}

# Construct three year return and join with ipo_return

gc()

ipo_return <-

ipo[date <= add_with_rollback(initial_date, months(36)), ][,.(three_year_ret = prod(1 + ret, na.rm = TRUE) - 1,
            three_year_excess_ret = prod(1 + ret_mkt, na.rm = TRUE) - 1), by = permno] %>%
            left_join(ipo_return, temp, by = c("permno" = "permno"))

```

```{r, message=FALSE, warning=FALSE}

# Remove ipo to save memory

rm(ipo)
gc()

```

```{r}

# Calculate descriptive statistics

columns_of_interest <-
  ipo_return %>%
  select(-permno) %>%
  colnames()

get_stats(ipo_return, NULL, columns_of_interest)

get_percentiles(ipo_return, NULL, columns_of_interest)

```






