---
title: "MGT 6090 Assignment 5 Part 1: MSF dataset"
author: "Yuguang Shen"
date: "September 28, 2021"
output:
  pdf_document: default
  html_document: default
---

```{r, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidyquant)
library(lubridate)
library(janitor)
library(corrplot)
library(data.table)
library(patchwork)
library(gt)
library(knitr)
library(RColorBrewer)

```

# Useful Functions

```{r}

# Function to calculate n, mean, sd, ect

get_stats <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_n" = ~n(),
                        "_mean" = ~mean(., na.rm = TRUE), 
                        "_sd" = ~sd(., na.rm = TRUE),
                        "_skew" = ~skewness(., na.rm = TRUE),
                        "_kurt" = ~kurtosis(., na.rm = TRUE),
                        "_min" = ~min(., na.rm = TRUE),
                        "_max" = ~max(., na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "n, mean, sd, skewness, kurtosis, min, max") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = mean:max, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  
  return (stats_table)
  
  
}

# Function to calculate percentile

get_percentiles <- function(my_df, col_0 = NULL, col_1) {
  
  
  stats_table <-
    my_df %>%
    group_by(across(all_of(col_0))) %>%
    summarise(across(all_of(col_1), 
                   list("_P1" = ~quantile(.,0.01, na.rm = TRUE),
                        "_P5" = ~quantile(.,0.05, na.rm = TRUE),
                        "_P25" = ~quantile(.,0.25, na.rm = TRUE),
                        "_P50" = ~quantile(.,0.5, na.rm = TRUE),
                        "_P75" = ~quantile(.,0.75, na.rm = TRUE),
                        "_P95" = ~quantile(.,0.95, na.rm = TRUE),
                        "_P99" = ~quantile(.,0.99, na.rm = TRUE)
                        ))) %>%
    
    pivot_longer(-c(all_of(col_0)), names_to = c("var", ".value"), names_sep = "__") %>% 
    
    arrange(var) %>%
    
    gt(rowname_col = col_0[1], groupname_col = "var") %>%
    
    tab_header(title = "Descriptive Statistics",
               subtitle = "percentiles") %>%
    
    tab_stubhead(label = col_0[1]) %>%
           
    cols_align(align = "center", columns = everything()) %>%
    
    fmt_number(columns = P1:P99, decimals = 4) %>%
    
    tab_options(
    column_labels.border.bottom.color = "black",
    column_labels.border.bottom.width= px(3),
    column_labels.border.top.color = "black",
    column_labels.border.top.width= px(3),
    
    row_group.border.top.style = NULL,
    row_group.border.top.width = px(3),
    row_group.border.top.color = "black",
    row_group.border.bottom.style = NULL,
    row_group.border.bottom.width = px(3),
    row_group.border.bottom.color = "black"

    )

  
  return (stats_table)
  
  
}

```

# Using MSF dataset

## 1. Load msf file

```{r, message=FALSE, warning=FALSE}

msf <-
  read_csv("msf_new2.csv", guess_max = 5000) %>%
  select(PERMNO, DATE, SHRCD, HEXCD, HSICCD, PRC, ALTPRC, RET, SHROUT, VWRETD) %>%
  filter(SHRCD %in% c(10, 11)) %>%
  clean_names() %>%
  mutate(date = ymd(date),
         prc = abs(prc),
         altprc = abs(altprc),
         ret = as.numeric(ret)
         ) %>%
  mutate(prc = case_when(is.na(prc) & !is.na(altprc) ~ altprc,
                         TRUE ~ prc))
  
```

## 2. Calculate Market Cap (in millions)

```{r, message=FALSE, warning=FALSE}

msf <-
  msf %>%
  mutate(mktcap = prc * shrout * 1000 / 1000000) %>%
  mutate(date = ceiling_date(date, "months") - 1)

```

## 2. Adjust Market Cap for CPI

```{r, message=FALSE, warning=FALSE}

# Load CPI data

cpi <-
    "CPIAUCNS" %>%
  tq_get(get = "economic.data", from = "1913-01-01") %>%
  rename("fred_code" = "symbol", "monthly_cpi" = "price") %>%
  select(-fred_code) %>%
  mutate(date = ymd(date)) %>%
  mutate(date = ceiling_date(date, "months") - 1)

# Calculate average CPI for 2010

cpi_2010 <-
  cpi %>%
   filter(date >= "2010-01-31" & date <= "2010-12-31") %>%
   select(monthly_cpi) %>%
   colMeans()

# Merge CPI data with msf and adjust cpi based on 2010 level

msf <-
 left_join(msf, cpi, by = c("date" = "date")) 

msf <- 
  msf %>%
  mutate(monthly_cpi = monthly_cpi / cpi_2010 * 100)

# Adjust Market Cap to 2010 dollar

msf <-
  msf %>%
  mutate(mktcap_as_2010 = mktcap * 100 / monthly_cpi)

```

## 3. Label the Exchange and Industry for each entry

```{r, message=FALSE, warning=FALSE}

msf <-
msf %>%
  mutate(hexcd = case_when(hexcd == 1 ~ "NYSE",
                           hexcd == 2 ~ "NYSE MKT",
                           hexcd == 3 ~ "NASDAQ",
                           hexcd == 4 ~ "Arca",
                           TRUE ~ "Other")) %>%
  mutate(industry = case_when(hsiccd %in% c(1:999) ~ "Agricu,Forestry,Fishing",
                              hsiccd %in% c(1000:1499) ~ "Mining",
                              hsiccd %in% c(1500:1799) ~ "Construc",
                              hsiccd %in% c(2000:3999) ~ "Mfg",
                              hsiccd %in% c(4000:4999) ~ "Transp,other Util",
                              hsiccd %in% c(5000:5199) ~ "Wholesale",
                              hsiccd %in% c(5200:5999) ~ "Retail",
                              hsiccd %in% c(6000:6799) ~ "Fin,Insur,Real Est",
                              hsiccd %in% c(7000:8999) ~ "Services",
                              TRUE ~ "Public Admin")) 

```

## 4. Plot Market Cap, monthly, with respect to Exchange

```{r, message=FALSE, warning=FALSE}

options(scipen = 999)

msf %>%
  group_by(date, hexcd) %>%
  summarise(across(mktcap_as_2010, list("sum" = ~sum(., na.rm = TRUE)))) %>%
                                        
  ggplot(aes(x = date, y = mktcap_as_2010_sum / 1000 )) +
  geom_line(aes(color = hexcd)) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Monthly Market Cap by Exchange",
       x = "Date",
       y = "Mkt Cap in 2010 Dollar (millions)",
       color = "Exchange")

# Plot Market Cap in log10 scale 

msf %>%
  group_by(date, hexcd) %>%
  summarise(across(mktcap_as_2010, list("n" = ~n(),
                                        "sum" = ~sum(., na.rm = TRUE)))) %>%
  ggplot(aes(x = date, y = mktcap_as_2010_sum / 1000 )) +
  geom_line(aes(color = hexcd)) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Monthly Market Cap by Exchange, log10 scale",
       x = "Date",
       y = "Mkt Cap in 2010 Dollar (millions)-log10",
       color = "Exchange") +
  scale_y_log10()

```

## 5. Plot number of stocks, monthly, with respect to Exchange

```{r, message=FALSE, warning=FALSE}

options(scipen = 999)

msf %>%
  group_by(date, hexcd) %>%
  summarise(across(mktcap_as_2010, list("n" = ~n(),
                                 "sum" = ~sum(., na.rm = TRUE)))) %>%
  ggplot(aes(x = date, y = mktcap_as_2010_n)) +
  geom_line(aes(color = hexcd)) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Monthly Number of Stocks by Exchange",
       x = "Date",
       y = "Number of Stocks",
       color = "Exchange")

# Plot Number of Stocks in log10 scale

msf %>%
  group_by(date, hexcd) %>%
  summarise(across(mktcap_as_2010, list("n" = ~n(),
                                 "sum" = ~sum(., na.rm = TRUE)))) %>%
  ggplot(aes(x = date, y = mktcap_as_2010_n)) +
  geom_line(aes(color = hexcd)) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Monthly Number of Stocks by Exchange, log10 scale",
       x = "Date",
       y = "Number of Stocks-log10",
       color = "Exchange") +
  scale_y_log10()

```

## 6. Plot Market Cap, monthly, with respect to Industries

```{r, message=FALSE, warning=FALSE}

options(scipen = 999)

msf %>%
  group_by(date, industry) %>%
  summarise(across(mktcap_as_2010, list("sum" = ~sum(., na.rm = TRUE)))) %>%
  ggplot(aes(x = date, y = mktcap_as_2010_sum / 1000)) +
  geom_line(aes(color = industry)) +
  scale_color_brewer(palette = "Paired") +
  labs(title = "Monthly Market Cap by Industry",
       x = "Date",
       y = "Mkt Cap in 2010 Dollar (millions)",
       color = "Industry") 


```

## 7. Plot number of stocks, monthly, with respect to industry

```{r, message=FALSE, warning=FALSE}

msf %>%
  
  group_by(date, industry) %>%
  summarise(across(mktcap_as_2010, list("n" = ~n()))) %>%
  ggplot(aes(x = date, y = mktcap_as_2010_n)) +
  geom_line(aes(color = industry)) +
  scale_color_brewer(palette = "Paired") +
  labs(title = "Monthly Number of Stocks by Industry",
       x = "Date",
       y = "Number of Stocks",
       color = "Industry") 


```

## 8. Compute Excess return over Risk Free rate

```{r, message=FALSE, warning=FALSE}

rf_monthly <-
  read_csv("F-F_Research_Data_Factors.csv", skip = 3) %>%
  rename("date" = "X1") %>%
  filter(date > 2020) %>%
  mutate(date = ymd(paste(date, "01"))) %>%
  mutate(date = ceiling_date(date, "months") - 1) %>%
  clean_names() %>%
  select(date, rf)

```



```{r}

msf <-
  left_join(msf, rf_monthly, by = c("date" = "date")) 

msf <-
  msf %>%
  mutate(ret_rf = ret - rf / 100)

```


```{r}

# Descriptive stats for 1925~2020

msf %>%
  get_stats(NULL, "ret_rf")

msf %>%
  get_percentiles(NULL, "ret_rf")

```

```{r}

# Descriptive ststs for 1963~2020

msf %>%
  filter(date >= "1963-01-31") %>%
  get_stats(NULL, "ret_rf")

msf %>%
  filter(date >= "1963-01-31") %>%
  get_percentiles(NULL, "ret_rf")

```

```{r, message=FALSE, warning=FALSE}

ret_rf_stats_table <-
  msf %>%
  get_stats("date", "ret_rf")

ret_rf_stats_table$`_data` %>%
  select("date", "mean", "sd") %>% 
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) + 
  geom_line() +
  labs(title = "Monthly Mean and Sd of Excess Return over Risk Free Rate")



```

## 9. Calculate excess return over MKT

```{r}

msf <-
  
msf %>%
  mutate(ret_mkt = ret - vwretd,
         ret_mkt_log = log(1 + ret_mkt))

```

```{r}

# Descriptive stats for 1925~2020

msf %>%
  get_stats(NULL, c("ret_mkt", "ret_mkt_log"))

msf %>%
  get_percentiles(NULL, c("ret_mkt", "ret_mkt_log"))

```

```{r}

# Descriptive ststs for 1963~2020

msf %>%
  filter(date >= "1963-01-31") %>%
  get_stats(NULL, c("ret_mkt", "ret_mkt_log"))

msf %>%
  filter(date >= "1963-01-31") %>%
  get_percentiles(NULL, c("ret_mkt", "ret_mkt_log"))

```

```{r, message=FALSE, warning=FALSE}

ret_mkt_stats_table <-
  msf %>%
  get_stats("date", "ret_mkt")

ret_mkt_stats_table$`_data` %>%
  select("date", "mean", "sd") %>% 
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) + 
  geom_line() +
  labs(title = "Monthly Mean and Sd of Excess Return over Mkt Portfolio")

ret_mkt_log_stats_table <-
  msf %>%
  get_stats("date", "ret_mkt_log")

ret_mkt_log_stats_table$`_data` %>%
  select("date", "mean", "sd") %>% 
  pivot_longer(-date, names_to = "variable", values_to = "value") %>%
  ggplot(aes(date, value, colour = variable)) + 
  geom_line() +
  labs(title = "Monthly Mean and Sd of Excess Log Return over Mkt Portfolio")

```








































































































































































